---
title: "Relative Importance Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

The following code runs a relative importance analysis and relative weight analysis for a logistic regression. This R markdown is split into sections

1. Preparing data / assigning functions for analysis 

```{r setup, include=FALSE}
# Setup
#libraries

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, dplyr, haven,kableExtra,MASS,nnet,performance,fuzzySim, 
               boot, broom,aod,caret)
library(tinytex)
  #data stuff
library(tidyverse)
library(dplyr)
  #CSV/CAV files
library(haven)
  #EDA stuff
library(kableExtra)
library(MASS)
library(nnet)
library(performance)
library(fuzzySim) #FDR corrections
library(broom) #for tidy models
  library(aod) # Wald test
library(boot) #bootstrapping
#library(caret) #weight analysis???
options(knitr.table.format = "html") 

## Prepare Data For Analysis 

#### Import & Select data

path <-  ifelse(Sys.info()[[1]] == "Windows","/Users/troyh/OneDrive/Documents/R/Data/NHRVS_2019_2020_FINAL_weighted.sav",
       ifelse(Sys.info()[[1]] == "Darwin", "~/Desktop/Adams_lab/SPSS_stuff/NHRVS_2019_2020_FINAL_weighted.sav", 
              "¿¿Donde Estoy??"
       ))

### Import dataset 
NHRVS_2019 <- read_sav(path)


### Select and rename Variables
thesis_NHRVS <- dplyr::select(NHRVS_2019,
    #Background Variables __________
      caseid,weight,Age,Male_Gender,White_Race,SomeCollege_or_Higher,
      Married_Partnered,Income_60k_plus,YN_work,
      PCS_FINAL,MCS_FINAL,Weight_kg,BMI,
    #Military variables__________
      Combat_Veteran,Years_in_Military,Branch_5cat,Enlistment_status_3cat,
      MilitaryRank_3cat,
    #Mental Health Variables___________
      TOTAL_TRAUMAS,PM_PCL_31,MDD_POSITIVE_CURRENT,GAD_POSITIVE_CURRENT,SI_CURRENT,
      AUD_CURRENT,DUD_CURRENT,Concussion_PosScreen,tot_MHC,Any_MHC,
    #Physical health Variables_________
      ANY_ADL_DISABILITY,ANY_IADL_DISABILITY,Any_Disability,tot_phc,Any_PHC,Q22A_1,Q22A_2,
      Q22A_3,Q22A_4,Q22A_5,Q22A_6,Q22A_7,Q22A_8,Q22A_9,Q22A_10,Q22A_11,Q22B_1,
      Q22B_2,Q22B_3,Q22B_4,Q22B_5,
    #Exercise variables ___________
      godin_mild_winsor,godin_Mod_winsor,godin_Stren_winsor,HCS,HCS_Cats,
      godin_total_ac,god3cat,god2cat,GODIN_outliers)
    
#Rename variabes
thesis_NHRVS <- rename(thesis_NHRVS,
      MET_total = godin_total_ac,
      God_mild = godin_mild_winsor,
      God_mod = godin_Mod_winsor,
      God_stren = godin_Stren_winsor,
      College = SomeCollege_or_Higher,
      MCS = MCS_FINAL,
      PCS = PCS_FINAL,
      Arthritis = Q22A_1,
      Athsma =  Q22A_2,
      Cancer = Q22A_3,
      Chron_pain = Q22A_4,
      Liv_dis = Q22A_5,
      Diabetes = Q22A_6,
      Hrt_dis = Q22A_7,
      Hrt_atk = Q22A_8,
      High_chol = Q22A_9,
      High_bld_press = Q22A_10,
      Kid_dis = Q22A_11,
      Migrane = Q22B_1,
      MS = Q22B_2,
      Osteoporosis = Q22B_3,
      Rhum_arth = Q22B_4,
      Stroke = Q22B_5,
      PTSD_Current = PM_PCL_31,
      MDD_Current = MDD_POSITIVE_CURRENT,
      GAD_Current = GAD_POSITIVE_CURRENT,
      SI_Current = SI_CURRENT,
      AUD_Current = AUD_CURRENT,
      DUD_Current = DUD_CURRENT,
      Concussion_current = Concussion_PosScreen
)
# We need exercsie variables that are in MET minutes, not just HCS. 
# We also need to create demographic and health variables

thesis_NHRVS<- thesis_NHRVS %>%
  # First Create all of the variables
  mutate(thesis_NHRVS, 
    # Exercise variables
         Ex_time = (God_mild + God_mod + God_stren)*15,
            # Tells us how long people exercised for.
         MET_min = MET_total* 15,
         MET_min_W = ifelse(MET_min > 2500, 2500, MET_min),
            # Total METs per week times the duration of exercise
         Ex_rec = as.factor(ifelse(MET_min >= 500, "Sufficient", "Inufficient")),
            # Meeting activity levels (i.e., sufficient vs insufficient)
         Ex_3cat = as.factor(ifelse(MET_min < 290, 1,
                              ifelse(MET_min < 500 & MET_min >= 290, 2,3))),
         Ex_4cats = as.factor(ifelse(MET_min < 290, "Sed",
                              ifelse(MET_min < 500 & MET_min >= 290, "Mod",
                              ifelse(MET_min < 1000 & MET_min >= 500, "Active", 
                              ifelse(MET_min < 2000 & MET_min >= 1000, "Super", NA))))),
         Ex_3catW = as.factor(ifelse(MET_min_W < 290, 1,
                              ifelse(MET_min_W < 500 & MET_min_W >= 290, 2,3))),
         Ex_4catsW = as.factor(ifelse(MET_min_W < 290, "Sed",
                              ifelse(MET_min_W < 500 & MET_min_W >= 290, "Mod",
                              ifelse(MET_min_W < 1000 & MET_min_W >= 500, "Active", 
                              ifelse(MET_min_W < 2500 & MET_min_W >= 1000, "Super", NA))))),
# 3 godin (HCS) categories converted to MET_min 
    # Other Variables 
         HCS_win = (God_mod*5) + (God_stren*9),
         HCS3cat = as.factor(ifelse(HCS_win < 14, "Insufficient",
                              ifelse(HCS_win < 24 & HCS_win >= 290, "Moderate", "Active"))),
         Yr5_Military = as.factor(ifelse(Years_in_Military >= 5, "5+", "<5")),
         Active_PA = as.factor(ifelse(Ex_3cat == 3,1,0)),
         Moderate_PA = as.factor(ifelse(Ex_3cat == 2,1,0)),
         Insuf_PA = as.factor(ifelse(Ex_3cat == 2,1,0)),
         Total_HC = Any_Disability + Arthritis + Cancer + Chron_pain + Liv_dis +
                    Diabetes + Hrt_dis + Hrt_atk + High_chol + High_bld_press +
                    Kid_dis + Migrane + MS + Osteoporosis + Rhum_arth + Stroke +
                    PTSD_Current + MDD_Current + GAD_Current + AUD_Current + DUD_Current,
         Total_PHC = Any_Disability + Arthritis + Cancer + Chron_pain + Liv_dis +
                    Diabetes + Hrt_dis + Hrt_atk + High_chol + High_bld_press +
                    Kid_dis + Migrane + MS + Osteoporosis + Rhum_arth + Stroke,
         Total_MHC = PTSD_Current + MDD_Current + GAD_Current + AUD_Current + DUD_Current,
         No_Condition = ifelse(Any_MHC == 1 | Any_PHC ==1, 0,1)
    
    ) %>%
mutate(thesis_NHRVS,
      #Physical health variables
           Any_Disability = as.factor(Any_Disability),
           Arthritis = as.factor(Arthritis),
           Athsma = as.factor(Athsma),
           Cancer = as.factor(Cancer),
           Chron_pain = as.factor(Chron_pain),
           Liv_dis = as.factor(Liv_dis),
           Diabetes = as.factor(Diabetes),
           Hrt_dis = as.factor(Hrt_dis),
           Hrt_atk = as.factor(Hrt_atk),
           High_chol = as.factor(High_chol),
           High_bld_press = as.factor(High_bld_press),
           Kid_dis = as.factor(Kid_dis),
           Migrane = as.factor(Migrane),
           MS = as.factor(MS),
           Osteoporosis = as.factor(Osteoporosis),
           Rhum_arth = as.factor(Rhum_arth),
           Stroke = as.factor(Stroke),
           Ex_3cat = as.factor(Ex_3cat),  
           Male_Gender = as.factor(Male_Gender), 
           Married_Partnered = as.factor(Married_Partnered),
           White_Race = as.factor(White_Race),
           College = as.factor(College),
           Income_60k_plus = as.factor(Income_60k_plus),
           YN_work = as.factor(YN_work),
           Combat_Veteran = as.factor(Combat_Veteran),
           Any_MHC = as.factor(Any_MHC),
           Any_PHC = as.factor(Any_PHC),
           god2cat = as.factor(god2cat),
      #Mental health variables
          PTSD_Current = as.factor(PTSD_Current),
          MDD_Current = as.factor(MDD_Current),
          GAD_Current = as.factor(GAD_Current),
          # SI_Current = SI_CURRENT,
          AUD_Current = as.factor(AUD_Current),
          DUD_Current = as.factor(DUD_Current),
    )
thesis_NHRVS <- mutate(thesis_NHRVS, 
        Ex_3cat = recode(Ex_3cat,
                         "1" = "Insufficient",
                         "2" = "Moderate",
                         "3" = "Active"),
        Married_Partnered = recode(Married_Partnered,
                         "0" = "Married_Partnered",
                         "1" = "Single"),
        Male_Gender = as.factor(Male_Gender),
        Male_Gender = recode(Male_Gender,
                         "0" = "Female",
                         "1" = "Male"),
        White_Race = recode(White_Race,
                         "0" = "Not_White",
                         "1" = "White"),
        College = recode(College,
                         "0" = "No_Colege",
                         "1" = "Some_Colege"),
        Income_60k_plus = recode(Income_60k_plus,
                         "0" = "Under_60k",
                         "1" = "OVer_60k"),
        YN_work = recode(YN_work,
                         "1" = "No_Work",
                         "2" = "Working"),
        Combat_Veteran = as.factor(Combat_Veteran),
        Combat_Veteran = recode(Combat_Veteran,
                         "0" = "No_Combat",
                         "1" = "Combat"),
        Any_MHC = recode(Any_MHC,
                         "0" = "No_con",
                         "1" = "MHC"),
        Any_PHC = recode(Any_PHC,
                         "0" = "No_con",
                         "1" = "PHC"))

#Filter out NA values
thesis_NHRVS <- thesis_NHRVS %>%
  filter(!is.na(Ex_rec)) %>%
  filter(!is.na(Ex_3cat)) %>%
  filter(!is.na(MCS)) %>%
  filter(!is.na(PCS)) %>%
  filter(!is.na(BMI)) %>%
  filter(!is.na(Any_Disability)) %>%
  filter(!is.na(Arthritis)) %>%
  filter(!is.na(Cancer)) %>%
  filter(!is.na(Chron_pain)) %>%
  filter(!is.na(Liv_dis)) %>%
  filter(!is.na(Diabetes)) %>%
  filter(!is.na(Hrt_dis)) %>%
  filter(!is.na(Hrt_atk)) %>%
  filter(!is.na(High_chol)) %>%
  filter(!is.na(High_bld_press)) %>%
  filter(!is.na(Kid_dis)) %>%
  filter(!is.na(Migrane)) %>%
  filter(!is.na(MS)) %>%
  filter(!is.na(Osteoporosis)) %>%
  filter(!is.na(Rhum_arth)) %>%
  filter(!is.na(Stroke)) %>%
  filter(!is.na(MDD_Current)) %>%
  filter(!is.na(PTSD_Current)) %>%
  filter(!is.na(AUD_Current)) %>%
  filter(!is.na(DUD_Current)) %>%
  filter(!is.na(GAD_Current)) |>
  mutate(Obesity = ifelse(is.na(BMI), NA,
      ifelse(BMI >=30,1,0)),
      Obesity = as.factor(Obesity)
           ) 
```

# Prep data / functions

## {.tabset}

### Create df for RIA analysis

slect statistically significant variables from logistic regression analysis
```{r df selection}
mydata <- thesis_NHRVS |>
    mutate(Obesity = ifelse(is.na(BMI), NA,
      ifelse(BMI >=30,1,0))
    ) |>
  #Select all of the variables needed for the analysis
  dplyr::select(
    #DV
       Ex_rec,
    #Covariates
       Age,College,
       Income_60k_plus,
    #Physical Health Conditions
       Athsma, Diabetes, Obesity,
    #Mental Health conditions
      DUD_Current, GAD_Current, MDD_Current, 
  )|>
    # Convert all of the varaibles to numeric
    mutate(
      Ex_rec = as.numeric(Ex_rec),
      Age = as.numeric(Age),
      College = as.numeric(College),
      Income_60k_plus = as.numeric(Income_60k_plus),
      Obesity = as.numeric(Obesity),
      Athsma = as.numeric(Athsma),
      Diabetes = as.numeric(Diabetes),
      DUD_Current = as.numeric(DUD_Current), 
      GAD_Current = as.numeric(GAD_Current),
      MDD_Current = as.numeric(MDD_Current), 
      
    )
#filter out missing data
mydata <- na.omit(mydata)
```


### Functions for bootstrapping
```{r Functions}
#### 1. logRegress -  LOGISTIC REGRESSION
# manually calculate Logistic Regression and obtain epsilon (i.e., raw relative
# R2o weight) and rescaled weights (i.e., epsilon / total R2o). The rescaled 
# weights are the relative percent of the R2o for each predictor. the rescaled
# weights add up to 100 as it is adding up to 100% of the variance explained.
logRegress<-function(mydata){
numVar<-NCOL(mydata)
Variables<-names(mydata)[2:numVar]
Y<-mydata[,1]
data.preds<-mydata[,2:length(mydata[1,])]
X<-scale(data.preds)

str(X)

X.svd<-svd(X)
Q<-X.svd$v
P<-X.svd$u
Z<-P%*%t(Q)

Z.stand<-scale(Z)

#Obtaining Lambda from equation 7 from Johnson (2000) pg 8
Lambda<-solve(t(Z.stand)%*%Z.stand)%*%t(Z.stand)%*%X

logrfit<-glm(as.factor(Y$Ex_rec)~Z.stand,family=binomial)
summary(logrfit)
unstCoefs<-coef(logrfit)
b<-unstCoefs[2:length(unstCoefs)]
LpredY<-predict(logrfit,newdata=mydata,type="response")
lYhat<-log(LpredY/(1-LpredY))#Creating logit-Y-hat
stdlYhat<-sd(lYhat)#Getting stdev of logit-Y-hat
getting.Rsq<-lm(LpredY~as.factor(Y$Ex_rec))#Getting R-sq
Rsq<-summary(getting.Rsq)$r.squared
beta<-b*((sqrt(Rsq))/stdlYhat)#Computing standardized logistic regression coefficients

epsilon<-Lambda^2%*%beta^2
R.sq<<-sum(epsilon)
PropWeights<-(epsilon/R.sq)
result <- data.frame(Variables, Raw.RelWeight=epsilon, Rescaled.RelWeight=PropWeights)
return(result)
}

#### 2. logBootstrap - BOOTSTRAP FOR RAW WEIGHTS
# This returns the bootstrapped Raw weights
# this function also calculates the bootstrapped bias and standard error
logBootstrap<-function(mydata, indices){
mydata<-mydata[indices,]
logWeights<-logRegress(mydata)
return(logWeights$Raw.RelWeight)
}

#### 3. logBootstrap_adj - BOOTSTRAP FOR RELATIVE WEIGHTS
# Same as funciton as above, but this function returns the boostrapped rescaled weights
logBootstrap_adj<-function(mydata, indices){
mydata<-mydata[indices,]
logWeights<-logRegress(mydata)
return(logWeights$Rescaled.RelWeight)
}

#### 4. logBootrand - BOOSTRAP FOR RANDOM VARAIBLE?
# I'm not sure what this is used for. Comparing if a variable is better than the 
# random variable? I can't get this function to work as it just tells me it has 
# missing variables dispite not actually having missing variables
logBootrand<-function(mydata, indices){
mydata<-mydata[indices,]
logRWeights<-logRegress(mydata)
logReps<-logRWeights$Raw.RelWeight
randWeight<-logReps[length(logReps)]
randStat<-logReps[-(length(logReps))]-randWeight
return(randStat)
}

#### 4. logBootrand_adj - BOOSTRAP FOR RANDOM VARAIBLE?
# I'm not sure what this is used for. Comparing if a variable is better than the 
# random variable? I can't get this function to work as it just tells me it has 
# missing variables dispite not actually having missing variables
logBootrand_adj<-function(mydata, indices){
mydata<-mydata[indices,]
logRWeights<-logRegress(mydata)
logReps<-logRWeights$Rescaled.RelWeight
randWeight<-logReps[length(logReps)]
randStat<-logReps[-(length(logReps))]-randWeight
return(randStat)
}

#### 5. mybootci -  EXTRACT THJE 95% CI'S 
# Extracts the  95% BCa ci for a given variable (i.e., index)
mybootci<-function(x){
boot.ci(logBoot,conf=0.95, type="bca", index=x)
}

#### 6. runBoot - EXTRACT THE 95% CI'S FOR EACH VARIABLE
# This function extracts the CI's for each given varaible in the bootstrap and 
# returns a df called test2 which contains the CI's and some other stats.
runBoot<-function(num){
INDEX<-1:num
test<-lapply(INDEX, FUN=mybootci)
test
test2<-t(sapply(test,'[[',i=4))
return(test2)
# CIresult<<-data.frame(Variables = coln, CI.Lower.Bound=test2[,4],CI.Upper.Bound=test2[,5])
}

#### 7. myRbootci - EXTRACT 95% CI W/RANDOM VARIABLE
# HAvent been able to get this to work, I think its the same as above, but w/
# a random variable?
myRbootci<-function(x){
boot.ci(logRBoot,conf=0.95,type="bca",index=x)
}

#### 8. runRBoot - EXTRACT THE 95% CI FOR EACH VARIABLE W/RANDOM
# HAvent been able to get this to work, I think its the same as above, but w/
# a random variable?
runRBoot<-function(num){
INDEX<-1:num
test<-lapply(INDEX,FUN=myRbootci)
test2<-t(sapply(test,'[[',i=4))
return(test2)
}
```

# Running the Relative Importance Analysis / Relative Weight Analysis

## {.tabset}

### Part 1 RIA/RWA
The code below uses the functions above to caculate how important each variable 
is to the varaince Phsyical Activity.
```{r RIA}
#1.1 Run logRegress function
result <- logRegress(mydata)

#1.2 Save results from logRegress function
RW.Results<-result
RSQ.o<-R.sq

RW.Results <- result |>
  #order the varaibles based upon the scaled weights
  # arrange(-Rescaled.RelWeight) |>
  #create percent varaibles
  mutate(Rescaled.RelWeight.percent = round((Rescaled.RelWeight*100),2),
         Raw.percent = round(Raw.RelWeight*100,4)
  )

# 1.3 display results of relative weight analysis
knitr::kable(RW.Results) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

### Part 2 Bootstrapping RIA/RWA

Use bootstrapping functions to obtain 95% CI's for raw and rescaled weights.
```{r Bootstrap RIA 1,results='hide',warning=FALSE,message=FALSE,error=FALSE}
#2.1 Set seed for anlaysis
set.seed(6624)

#2.2 Boot function to bootstrap for raw weights CI
logBoot <-boot(mydata, # Data
              logBootstrap, # Statistic
              10000) # R / number of times

#2.3 Extract RIA/RWA statistic with bias and SE
tidy_boot <- tidy(logBoot)
  # You can obtain confidence intervals using the SE (+/-1.96*SE)
  #CI.Results_tidy <- tidy(logBoot_B3,conf.int=TRUE)

#2.4 assign the # of variables (columns) in mydata to a variable named numVar
numVar = NCOL(mydata)

#2.5 Run the boot.ci function to obtain the CI for the model
logci<-boot.ci(logBoot,conf=0.95, type="bca")

#2.6 Run runBoot function and extract 95% CI for the IV's in the model.
test2 <- runBoot(length(mydata[,2:numVar]))
```

Create df and export to csv so you don't need to run stats every time
```{r Bootstrap RIA 2,warning=FALSE,message=FALSE,error=FALSE}
#2.7 Create df with 95% CI
CI.Result<-data.frame(Variables=colnames(mydata[2:10]), CI.Lower.Bound=test2[,4],CI.Upper.Bound=test2[,5])

#2.8 Save df as a csv so you can call it again in the future
write_csv(CI.Result, "/Users/troyh/Downloads/CI.Result")
write_csv(tidy_boot, "/Users/troyh/Downloads/tidy_boot")



#2.9 Here is the output using tidy()
knitr::kable(tidy_boot) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

#2.10 here is the output using boot.ci() abnd runBoot()
knitr::kable(CI.Result) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

Run the same code again but for the rescaled weights
```{r Bootstrap RIA 3,results='hide',warning=FALSE,message=FALSE,error=FALSE}
#2.11 run bootstrap anlysis for rescaled CI so it can be used in figures
logBoot_adj <-boot(mydata, # Data
              logBootstrap_adj, # Statistic
              10000) # R / number of times

numVar = NCOL(mydata)
mydata <- mydata
logBoot <-logBoot_adj
logci<-boot.ci(logBoot,conf=0.95, type="bca")
numVar = length(mydata)
test2 <- runBoot(length(mydata[,2:numVar]))
tidy_boot_res <- tidy(logBoot_adj)
CI.Result.res<<-data.frame(Variables=colnames(mydata[2:10]), CI.Lower.Bound=test2[,4],CI.Upper.Bound=test2[,5])
write_csv(CI.Result.res, "/Users/troyh/Downloads/CI.Result.res")
write_csv(tidy_boot_res, "/Users/troyh/Downloads/tidy_boot_res")
```



The code below is used for significance testing. If the output has a negative value that variable is **not statistically significant**. This code adds a random varaible into the data frame, and runs the analysis with this as a reference for other variables.
```{r Random Boot function,results='hide',echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
#Bootstrapped Confidence interval tests of Significance
#Please be patient -- This can take a few minutes to run
logRegress<-function(mydata){
numVar<-NCOL(mydata)
Variables<-names(mydata)[2:numVar]
Y<-mydata[,1]
data.preds<-mydata[,2:length(mydata[1,])]
X<-scale(data.preds)

str(X)

X.svd<-svd(X)
Q<-X.svd$v
P<-X.svd$u
Z<-P%*%t(Q)

Z.stand<-scale(Z)

#Obtaining Lambda from equation 7 from Johnson (2000) pg 8
Lambda<-solve(t(Z.stand)%*%Z.stand)%*%t(Z.stand)%*%X 

logrfit<-glm(as.factor(Y)~Z.stand,family=binomial)
summary(logrfit)
unstCoefs<-coef(logrfit)
b<-unstCoefs[2:length(unstCoefs)]
LpredY<-predict(logrfit,newdata=mydata,type="response")
lYhat<-log(LpredY/(1-LpredY))#Creating logit-Y-hat
stdlYhat<-sd(lYhat)#Getting stdev of logit-Y-hat
getting.Rsq<-lm(LpredY~as.factor(Y))#Getting R-sq
Rsq<-summary(getting.Rsq)$r.squared
beta<-b*((sqrt(Rsq))/stdlYhat)#Computing standardized logistic regression coefficients

epsilon<-Lambda^2%*%beta^2
R.sq<<-sum(epsilon)
PropWeights<-(epsilon/R.sq)
result <- data.frame(Variables, Raw.RelWeight=epsilon, Rescaled.RelWeight=PropWeights)
return(result)
}
```


```{r Random Boot 1,results='hide',warning=FALSE,message=FALSE,error=FALSE}
#2.12 set seed for reproduceability
set.seed(6624)
#2.13 assign random variables with a mean of 0 and an SD of 1
randVar<-rnorm(length(mydata$Ex_rec), mean = 0, sd = 1)
#2.14 bind it to df
randData<-cbind(mydata,randVar)
#2.15 run random varaible bootstrap RIA
numVar = ncol(randData)
logRBoot<-boot(randData,logBootrand, 10000)
logRci<-boot.ci(logRBoot,conf=0.95, type="bca")
test2 <- runRBoot(length(randData[,2:(numVar-1)]))
#2.16 save output
CI.Result.rand <<-data.frame(Variables=colnames(mydata[2:10]), CI.Lower.Bound=test2[,4],CI.Upper.Bound=test2[,5])

#2.17 view results
knitr::kable(CI.Result.rand) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

Negative lower bound CI's indicate non significance. You can see that Athsma, DUD current, GAD current, and MDD current have **a negative lower bound CI**, resulting in these variables _not_ being significant. 

### Part 3 join results into on df and create variables for Figures

```{r rename df}
# CI.Result <- read.csv("/Users/troyh/Downloads/CI.Result")
# CI.Result.res <- read.csv("/Users/troyh/Downloads/CI.Result.res")
# tidy_boot_res <- read_csv("/Users/troyh/Downloads/tidy_boot_res")
# tidy_boot <- read_csv("/Users/troyh/Downloads/tidy_boot")

#BCa Confidence Intervals around the raw weights

# rename varaibles per analysis as Raw or Rescale
colnames(CI.Result) <- paste0(colnames(CI.Result),"_Raw")
colnames(CI.Result.res) <- paste0(colnames(CI.Result.res),"_Rescale")
```


```{r data wrangle}
#left join bootstraped results to RW.Results df
RW.Results <- left_join(RW.Results,CI.Result, by = join_by(Variables == Variables_Raw))
RW.Results <- left_join(RW.Results,CI.Result.res, by = join_by(Variables == Variables_Rescale))

#left join tidy bootstrap dataset
RW.Results <- left_join(RW.Results,tidy_boot_res, by = join_by(Rescaled.RelWeight == statistic))

#create new df with CIs and values as %
wt_df <- RW.Results |>
  mutate(
  # make raw values that are rounded and %'s
    raw.CI = paste0("[", round(CI.Lower.Bound_Raw*100,2), ", ", 
                    round(CI.Upper.Bound_Raw*100,2), "]"),
    raw.CI.low = round(CI.Lower.Bound_Raw*100,2),
    raw.CI.high = round(CI.Upper.Bound_Raw*100,2),
  # make rescale values that are rounded and %'s 
    res.CI = paste0("[", round(CI.Lower.Bound_Rescale*100,2), ", ", 
                    round(CI.Upper.Bound_Rescale*100,2), "]"),
    res.CI.low = round(CI.Lower.Bound_Rescale*100,2),
    res.CI.high = round(CI.Upper.Bound_Rescale*100,2),
  #make a variable that will be used as an order for figures
    order = NA,
  #make variabels that can be used for ggtext
    Raw.wt.text = round(Raw.percent,2),
    Res.wt.text = round(Rescaled.RelWeight.percent,2),
  #manually calculate CI's based upon SE from bootstrapped.
    res.CI.low.man.stat = (Rescaled.RelWeight - (1.96*std.error)),
    res.CI.high.man.stat = (Rescaled.RelWeight + (1.96*std.error)),
    res.CI.man = paste0("[", round(res.CI.low.man.stat*100,2), ", ", 
                    round(res.CI.high.man.stat*100,2), "]"),
    res.CI.low.man = round(res.CI.low.man.stat*100,2),
    res.CI.high.man = round(res.CI.high.man.stat*100,2)
  )

#assign variables and put them at the top
  wt_df[10,]   = NA  
  wt_df[10,1]  = "Variable"
  wt_df[10,12] = "95% CI"
  wt_df[10,15] = "95% CI"
  wt_df[10,19] = "R2o (%)"  
  wt_df[10,20] = "Rescaled (%)" 
  wt_df[10,23] = "95% CI"
  wt_df <- arrange(wt_df,-Rescaled.RelWeight)
  wt_df$order  = c(seq(2,10,1),1)
  wt_df <- arrange(wt_df,order)
  
```

# Visualize analysis with barplots

## {.tabset}

### Barplot w/ manual CI's

I used patchwork to combine `ggtext()` and the `geom_bar()` figures. The figure 
below is manually calculated 95% CI's for the rescaled weights using `tidy()` to extract the bootstrapped standard errors.

```{r fig 1,fig.width=8,warning=FALSE,message=FALSE}
wt_plot_man <- wt_df |>
  ggplot(aes(x=reorder(Variables,-order),y=Rescaled.RelWeight.percent)) +
  geom_bar(stat = "identity", color = "Black", width = .75, fill = "#91c3e6" )+
  geom_errorbar(aes(ymin=res.CI.low.man, ymax=res.CI.high.man,width =.3, show.legend = FALSE)) +
  labs(
    # title = "     Relative Weight (%) Of Predictors On Physical Activity",
    subtitle ="Relative Weight (%) Of Predictors On Physical Activity" 
      #"      RIA with 10000 bootstrapped confidence intervals"
  ) +
  theme_classic() +
  xlab('Variable')+
  ylab('Weight (%) of variance (R2o) in physical activity')+
  ylim(-3,50)+
  # geom_text(aes(label = wt_text), vjust =.5, hjust = -.1, color = "black")+
  coord_flip()  +
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

wt_text_man <- 
  wt_df |>
  ggplot(aes(y = reorder(Variables, -order))) +
  geom_text(aes(x = 0, label = Variables), hjust = 0, 
        fontface = ifelse(wt_df$Variables == "Variable", "bold","plain")) +
  geom_text(aes(x = 1.1, label = Res.wt.text),
        hjust = 0,
        fontface = ifelse(wt_df$Res.wt.text == "Rescaled (%)", "bold","plain")) +
  geom_text(aes(x = 2, label = res.CI.man),
        hjust = 0,
        fontface = ifelse(wt_df$res.CI.man == "95% CI", "bold","plain")) +
  theme_void() +     
  coord_cartesian(ylim = c(1,length(wt_df$Variables)), xlim = c(0, 4))
library("patchwork")
layout <- c(
  patchwork::area(t = 0, l = 0, b = 30, r = 30),
  patchwork::area(t = 0, l = 22, b = 30, r = 40)
)
```


```{r fig 2,fig.width=8}
wt_text_man + wt_plot_man + plot_layout(design = layout)
```

### Barplot w/ Robbs Code

This figure is the rescaled weights Barplot using my `mybootci()` and `runBoot()` to obtain the 95% CI. I can't figure out why the 95% CI is skewed.

```{r,fig.width=8,warning=FALSE,include=FALSE}
wt_plot <- 
  wt_df |>
  arrange(wt_df,order) |>
  ggplot(aes(x=stats::reorder(Variables,-order),y=Rescaled.RelWeight.percent)) +
  geom_bar(stat = "identity", color = "Black", width = .75, fill = "#91c3e6" )+
  geom_errorbar(aes(ymin=res.CI.low, ymax=res.CI.high,width =.3, show.legend = FALSE)) +
  labs(
    # title = "     Relative Weight (%) Of Predictors On Physical Activity",
    subtitle ="Relative Weight (%) Of Predictors On Physical Activity" 
      #"      RIA with 10000 bootstrapped confidence intervals"
  ) +
  theme_classic() +
  xlab('Variable')+
  ylab('Weight (%) of variance (R2o) in physical activity')+
  ylim(0,50)+
  # geom_text(aes(label = wt_text), vjust =.5, hjust = -.1, color = "black")+
  coord_flip()  +
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

wt_text <- 
  wt_df |>
  ggplot(aes(y = reorder(Variables, -order))) +
  geom_text(aes(x = 0, label = Variables), hjust = 0, 
        fontface = ifelse(wt_df$Variables == "Variable", "bold","plain")) +
  geom_text(aes(x = 1.1, label = Res.wt.text),
        hjust = 0,
        fontface = ifelse(wt_df$Res.wt.text == "Rescaled (%)", "bold","plain")) +
  geom_text(aes(x = 2, label = res.CI),
        hjust = 0,
        fontface = ifelse(wt_df$res.CI == "95% CI", "bold","plain")) +
  theme_void() +     
  coord_cartesian(ylim = c(1,length(wt_df$Variables)), xlim = c(0, 4))

library("patchwork")

layout <- c(
  patchwork::area(t = 0, l = 0, b = 30, r = 30),
  patchwork::area(t = 0, l = 22, b = 30, r = 40)
)
```


```{r,fig.width=8,warning=FALSE}
wt_text + wt_plot + plot_layout(design = layout)
```





