---
title: "Logistic Multinomial Regresion"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

The following code will show you how I created functions to run my multinomial regressions. This page includes:

1. Create function to run univariate multinomial regressions.
2. Run block 1 of the step wise multivariate multinomial regression.
3. Run block 2 of the step wise multivariate multinomial regression. 
4. Create function for block 3 of step wise multivariate multinomial regression.
5. Obtain R^2 values for each varaible in regressio model, and R^2 change between blocks of the stepwise regression
6. Run function for block 3 of the step wise multivariate multinomial regression.
7. Create table of output from stepwise regression model. 

--- 
```{r setup, include=FALSE}
# Setup
#libraries

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, dplyr, haven,kableExtra,MASS,nnet,performance,fuzzySim, 
               boot, broom,aod,caret)

  #data stuff
library(tidyverse)
library(dplyr)
  #CSV/CAV files
library(haven)
  #EDA stuff
library(kableExtra)
library(MASS)
library(nnet)
library(performance)
library(fuzzySim) #FDR corrections
library(broom) #for tidy models
  library(aod) # Wald test
library(boot) #bootstrapping
#library(caret) #weight analysis???
options(knitr.table.format = "html") 

## Prepare Data For Analysis 

#### Import & Select data
path <- "/Users/troyh/OneDrive/Documents/R/Data/NHRVS_2019_2020_FINAL_weighted.sav"



  ifelse(Sys.info()[[1]] == "Windows","/Users/troyh/OneDrive/Documents/R/Data/NHRVS_2019_2020_FINAL_weighted.sav",
       ifelse(Sys.info()[[1]] == "Darwin", "~/Desktop/Adams_lab/SPSS_stuff/NHRVS_2019_2020_FINAL_weighted.sav", "¿¿Donde Estoy??"
       ))

### Import dataset 
NHRVS_2019 <- read_sav(path)




### Select and rename Variables
thesis_NHRVS <- dplyr::select(NHRVS_2019,
    #Background Variables __________
      caseid,weight,Age,Male_Gender,White_Race,SomeCollege_or_Higher,
      Married_Partnered,Income_60k_plus,YN_work,
      PCS_FINAL,MCS_FINAL,Weight_kg,BMI,
    #Military variables__________
      Combat_Veteran,Years_in_Military,Branch_5cat,Enlistment_status_3cat,
      MilitaryRank_3cat,
    #Mental Health Variables___________
      TOTAL_TRAUMAS,PM_PCL_31,MDD_POSITIVE_CURRENT,GAD_POSITIVE_CURRENT,SI_CURRENT,
      AUD_CURRENT,DUD_CURRENT,Concussion_PosScreen,tot_MHC,Any_MHC,
    #Physical health Variables_________
      ANY_ADL_DISABILITY,ANY_IADL_DISABILITY,Any_Disability,tot_phc,Any_PHC,Q22A_1,Q22A_2,
      Q22A_3,Q22A_4,Q22A_5,Q22A_6,Q22A_7,Q22A_8,Q22A_9,Q22A_10,Q22A_11,Q22B_1,
      Q22B_2,Q22B_3,Q22B_4,Q22B_5,
    #Exercise variables ___________
      godin_mild_winsor,godin_Mod_winsor,godin_Stren_winsor,HCS,HCS_Cats,
      godin_total_ac,god3cat,god2cat,GODIN_outliers)
    
#Rename variabes
thesis_NHRVS <- rename(thesis_NHRVS,
      MET_total = godin_total_ac,
      God_mild = godin_mild_winsor,
      God_mod = godin_Mod_winsor,
      God_stren = godin_Stren_winsor,
      College = SomeCollege_or_Higher,
      MCS = MCS_FINAL,
      PCS = PCS_FINAL,
      Arthritis = Q22A_1,
      Athsma =  Q22A_2,
      Cancer = Q22A_3,
      Chron_pain = Q22A_4,
      Liv_dis = Q22A_5,
      Diabetes = Q22A_6,
      Hrt_dis = Q22A_7,
      Hrt_atk = Q22A_8,
      High_chol = Q22A_9,
      High_bld_press = Q22A_10,
      Kid_dis = Q22A_11,
      Migrane = Q22B_1,
      MS = Q22B_2,
      Osteoporosis = Q22B_3,
      Rhum_arth = Q22B_4,
      Stroke = Q22B_5,
      PTSD_Current = PM_PCL_31,
      MDD_Current = MDD_POSITIVE_CURRENT,
      GAD_Current = GAD_POSITIVE_CURRENT,
      SI_Current = SI_CURRENT,
      AUD_Current = AUD_CURRENT,
      DUD_Current = DUD_CURRENT,
      Concussion_current = Concussion_PosScreen
)
# We need exercsie variables that are in MET minutes, not just HCS. 
# We also need to create demographic and health variables

thesis_NHRVS<- thesis_NHRVS %>%
  # First Create all of the variables
  mutate(thesis_NHRVS, 
    # Exercise variables
         Ex_time = (God_mild + God_mod + God_stren)*15,
            # Tells us how long people exercised for.
         MET_min = MET_total* 15,
         MET_min_W = ifelse(MET_min > 2500, 2500, MET_min),
            # Total METs per week times the duration of exercise
         Ex_rec = as.factor(ifelse(MET_min >= 500, "Sufficient", "Inufficient")),
            # Meeting activity levels (i.e., sufficient vs insufficient)
         Ex_3cat = as.factor(ifelse(MET_min < 290, 1,
                              ifelse(MET_min < 500 & MET_min >= 290, 2,3))),
         Ex_4cats = as.factor(ifelse(MET_min < 290, "Sed",
                              ifelse(MET_min < 500 & MET_min >= 290, "Mod",
                              ifelse(MET_min < 1000 & MET_min >= 500, "Active", 
                              ifelse(MET_min < 2000 & MET_min >= 1000, "Super", NA))))),
         Ex_3catW = as.factor(ifelse(MET_min_W < 290, 1,
                              ifelse(MET_min_W < 500 & MET_min_W >= 290, 2,3))),
         Ex_4catsW = as.factor(ifelse(MET_min_W < 290, "Sed",
                              ifelse(MET_min_W < 500 & MET_min_W >= 290, "Mod",
                              ifelse(MET_min_W < 1000 & MET_min_W >= 500, "Active", 
                              ifelse(MET_min_W < 2500 & MET_min_W >= 1000, "Super", NA))))),
# 3 godin (HCS) categories converted to MET_min 
    # Other Variables 
         HCS_win = (God_mod*5) + (God_stren*9),
         HCS3cat = as.factor(ifelse(HCS_win < 14, "Insufficient",
                              ifelse(HCS_win < 24 & HCS_win >= 290, "Moderate", "Active"))),
         Yr5_Military = as.factor(ifelse(Years_in_Military >= 5, "5+", "<5")),
         Active_PA = as.factor(ifelse(Ex_3cat == 3,1,0)),
         Moderate_PA = as.factor(ifelse(Ex_3cat == 2,1,0)),
         Insuf_PA = as.factor(ifelse(Ex_3cat == 2,1,0)),
         Total_HC = Any_Disability + Arthritis + Cancer + Chron_pain + Liv_dis +
                    Diabetes + Hrt_dis + Hrt_atk + High_chol + High_bld_press +
                    Kid_dis + Migrane + MS + Osteoporosis + Rhum_arth + Stroke +
                    PTSD_Current + MDD_Current + GAD_Current + AUD_Current + DUD_Current,
         Total_PHC = Any_Disability + Arthritis + Cancer + Chron_pain + Liv_dis +
                    Diabetes + Hrt_dis + Hrt_atk + High_chol + High_bld_press +
                    Kid_dis + Migrane + MS + Osteoporosis + Rhum_arth + Stroke,
         Total_MHC = PTSD_Current + MDD_Current + GAD_Current + AUD_Current + DUD_Current,
         No_Condition = ifelse(Any_MHC == 1 | Any_PHC ==1, 0,1)
    
    ) %>%
mutate(thesis_NHRVS,
      #Physical health variables
           Any_Disability = as.factor(Any_Disability),
           Arthritis = as.factor(Arthritis),
           Athsma = as.factor(Athsma),
           Cancer = as.factor(Cancer),
           Chron_pain = as.factor(Chron_pain),
           Liv_dis = as.factor(Liv_dis),
           Diabetes = as.factor(Diabetes),
           Hrt_dis = as.factor(Hrt_dis),
           Hrt_atk = as.factor(Hrt_atk),
           High_chol = as.factor(High_chol),
           High_bld_press = as.factor(High_bld_press),
           Kid_dis = as.factor(Kid_dis),
           Migrane = as.factor(Migrane),
           MS = as.factor(MS),
           Osteoporosis = as.factor(Osteoporosis),
           Rhum_arth = as.factor(Rhum_arth),
           Stroke = as.factor(Stroke),
           Ex_3cat = as.factor(Ex_3cat),  
           Male_Gender = as.factor(Male_Gender), 
           Married_Partnered = as.factor(Married_Partnered),
           White_Race = as.factor(White_Race),
           College = as.factor(College),
           Income_60k_plus = as.factor(Income_60k_plus),
           YN_work = as.factor(YN_work),
           Combat_Veteran = as.factor(Combat_Veteran),
           Any_MHC = as.factor(Any_MHC),
           Any_PHC = as.factor(Any_PHC),
           god2cat = as.factor(god2cat),
      #Mental health variables
          PTSD_Current = as.factor(PTSD_Current),
          MDD_Current = as.factor(MDD_Current),
          GAD_Current = as.factor(GAD_Current),
          # SI_Current = SI_CURRENT,
          AUD_Current = as.factor(AUD_Current),
          DUD_Current = as.factor(DUD_Current),
    )
thesis_NHRVS <- mutate(thesis_NHRVS, 
        Ex_3cat = recode(Ex_3cat,
                         "1" = "Insufficient",
                         "2" = "Moderate",
                         "3" = "Active"),
        Married_Partnered = recode(Married_Partnered,
                         "0" = "Married_Partnered",
                         "1" = "Single"),
        Male_Gender = as.factor(Male_Gender),
        Male_Gender = recode(Male_Gender,
                         "0" = "Female",
                         "1" = "Male"),
        White_Race = recode(White_Race,
                         "0" = "Not_White",
                         "1" = "White"),
        College = recode(College,
                         "0" = "No_Colege",
                         "1" = "Some_Colege"),
        Income_60k_plus = recode(Income_60k_plus,
                         "0" = "Under_60k",
                         "1" = "OVer_60k"),
        YN_work = recode(YN_work,
                         "1" = "No_Work",
                         "2" = "Working"),
        Combat_Veteran = as.factor(Combat_Veteran),
        Combat_Veteran = recode(Combat_Veteran,
                         "0" = "No_Combat",
                         "1" = "Combat"),
        Any_MHC = recode(Any_MHC,
                         "0" = "No_con",
                         "1" = "MHC"),
        Any_PHC = recode(Any_PHC,
                         "0" = "No_con",
                         "1" = "PHC"))

#Filter out NA values
thesis_NHRVS <- thesis_NHRVS %>%
  filter(!is.na(Ex_rec)) %>%
  filter(!is.na(Ex_3cat)) %>%
  filter(!is.na(MCS)) %>%
  filter(!is.na(PCS)) %>%
  filter(!is.na(BMI)) %>%
  filter(!is.na(Any_Disability)) %>%
  filter(!is.na(Arthritis)) %>%
  filter(!is.na(Cancer)) %>%
  filter(!is.na(Chron_pain)) %>%
  filter(!is.na(Liv_dis)) %>%
  filter(!is.na(Diabetes)) %>%
  filter(!is.na(Hrt_dis)) %>%
  filter(!is.na(Hrt_atk)) %>%
  filter(!is.na(High_chol)) %>%
  filter(!is.na(High_bld_press)) %>%
  filter(!is.na(Kid_dis)) %>%
  filter(!is.na(Migrane)) %>%
  filter(!is.na(MS)) %>%
  filter(!is.na(Osteoporosis)) %>%
  filter(!is.na(Rhum_arth)) %>%
  filter(!is.na(Stroke)) %>%
  filter(!is.na(MDD_Current)) %>%
  filter(!is.na(PTSD_Current)) %>%
  filter(!is.na(AUD_Current)) %>%
  filter(!is.na(DUD_Current)) %>%
  filter(!is.na(GAD_Current)) |>
  mutate(Obesity = ifelse(is.na(BMI), NA,
      ifelse(BMI >=30,1,0)),
      Obesity = as.factor(Obesity)
           ) 
  
#$View(thesis_NHRVS)


```


# Preliminary Regression: Univariate Regression function

The first step in my analysis was to run the multinomial regressions without covariates so I can see how the health conditions are associated with physical activity level independent of covariates. The following `UniThesis()` function does the following:

1. Runs the multinomial models using `multinom()`
2. Manually calculates the coefficients _B_, the odds ratios (OR) + 95% Confideince interval (95% CI), and _p_ values
3. Extracts respective values for each type of comparison (e.g., sufficiently active vs moderatly active)
4. Returns respective values as a row in a data frame which can be compiled into a larger data frame per comparison

# Step Wise Multivariate Logistic Multinomial Regression
That's a mouthful! For the following section we will be running code for the full regression model, The blocks of this regession are as follows:

1. Covariates: Sociodemograpahic, military, and health variables
2. Physical health conditions
3. Mental Health Conditions

## Regession Code {.tabset}

### Block 1: Covariates
This first block of the stepwise regression will do the same thing as we did for the univariate analysis, being that this was not replicated we did not make a function for it.

```{r,warning=FALSE,message=FALSE,results='hide'}
### Part 1 Create values for table
#1. Run the models
Cov_Reg<-glm(Ex_rec~ + Age + College + White_Race  + Income_60k_plus + Combat_Veteran + 
                           TOTAL_TRAUMAS, data= thesis_NHRVS,family="binomial") 
  

Cov_Reg_sum <- summary(Cov_Reg)
Cov_Reg_sum <- tidy(Cov_Reg) 

#2. Coefficients 
  coefs_Cov_Reg <- abs(coef(Cov_Reg))
  coefs_Cov_Reg 
#3. Odds ratio
  OR_Cov_Reg <- exp(coef(Cov_Reg))

#4. OR 95% CI
  CI_Cov_Reg <- data.frame(round(exp(confint(Cov_Reg)),2))

#5. P values 
  p_val1<- cbind(Cov_Reg_sum$term ,Cov_Reg_sum$p.value)
    adj.p <- FDR(pvalues = p_val1)
    ADJ.p.values <- data.frame(rbind(adj.p$exclude, adj.p$select))
    ADJ.p.values
    
#6. R^2 for model
  R2_Cov_Reg <- performance::r2(Cov_Reg)

#wald

  cov_wald<- wald.test(b = coef(Cov_Reg),Sigma = vcov(Cov_Reg),Terms= 2:7)
  cov_wald$result$chi2[1]
  wald <- wald.test(b = coef(Cov_Reg),Sigma = vcov(Cov_Reg),Terms=2)$result$chi2[1]
  for(i in 3:7){
      wald <- append(wald, wald.test(b = coef(Cov_Reg),Sigma = vcov(Cov_Reg),Terms=i)$result$chi2[1])
  }
  wald
#### Part 2. Make the table and export 

#1. Create data frame
cov_OR_df <-  data.frame(cbind(
  variable = Cov_Reg_sum$term[2:length(Cov_Reg_sum$term)],
  Beta = coefs_Cov_Reg[2:length(Cov_Reg_sum$term)],
  Wald = round(wald,2),
  OR = OR_Cov_Reg[2:length(OR_Cov_Reg)],
  CI = paste0("[",CI_Cov_Reg[2:length(OR_Cov_Reg),1], ",", CI_Cov_Reg[2:length(OR_Cov_Reg),2], "]"),
  p = p_val1[2:7,2]
))


cov_OR_df  <- left_join(cov_OR_df, ADJ.p.values,by = join_by(p == p.value))
cov_OR_tab <- data.frame(cbind(
  variable = cov_OR_df$variable,
  Beta = cov_OR_df$Beta,
  Wald = cov_OR_df$Wald,
  OR = cov_OR_df$OR,
  CI = cov_OR_df$CI,
  p = cov_OR_df$p.adjusted
))

cov_OR_tab$Beta = round(as.numeric(cov_OR_tab$Beta),2)
cov_OR_tab$Wald = round(as.numeric(cov_OR_tab$Wald),2)
cov_OR_tab$OR = round(as.numeric(cov_OR_tab$OR),2)
cov_OR_tab$p = ifelse(as.numeric(cov_OR_df$p) < 0.001, "< 0.001",
  round(as.numeric(cov_OR_df$p),3))

#2. create the row for the R2
  paste("Block 1 R^2 =", round((R2_Cov_Reg[[1]]*100),3),"%")
  variable = c(
    "Block 1 - Covariates",
    paste0("X^2=", round(cov_wald$result$chi2[1],2),",p<0.001"),
    paste0("R^2=", round((R2_Cov_Reg[[1]]),3))  
  )



  R2TAB<-data.frame(cbind(
                      variable,Beta=NA,Wald=NA, OR =NA, CI=NA, p=NA))

#3. Bind the stuff together
  cov_OR_tab <- rbind(R2TAB, cov_OR_tab)
cov_OR_tab
#4. Export
  # write_csv(cov_OR_tab,"~/Desktop/Coding/data/EX_C_cov_OR_tab.csv")
```
```{r}
  knitr::kable(cov_OR_tab) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Full Model Function

The final step in my analysis was to run the full multinomial model so I can see how the health conditions are associated with physical activity level after controling for covariates. The following `MultiThesis()` function does the following 
1. Runs the 2 different multinomial models using [multinom()](https://www.rdocumentation.org/packages/nnet/versions/7.3-18/topics/multinom)
    + Physical health condtions include the MCS
    + Mental health conditions include the PCS
2. Manually calculates the coefficients _B_, the odds ratios (OR) + 95% Confideince interval (95% CI), and _p_ values
3. Extracts respective values for each type of comparison (e.g., sufficiently active vs moderatly active)
4. Returns respective values as a row in a dataframe which can be compiled into a larger data fram per comparison


Make a function to run a chi2 and save the output for all physical health conditions
```{r}
Condition_eval<-function(condition,string){
  chi2 <- xtabs(~thesis_NHRVS$Ex_rec + condition)
  output <- data.frame(cbind(
    variable = string, 
    chi2 = summary(chi2)[[3]], 
    p = summary(chi2)[[6]]
  ))
  return(output)
}
```


Run the chi2 function to get an output of what variables we should include in our regression model
```{r,include=FASLSE}
#1. run model 1
Conditions_chi<-data.frame(Condition_eval(thesis_NHRVS$Arthritis,"Arthritis"))
#3. Asthma
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Athsma,"Athsma"))
#4. Cancer
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Cancer,"Cancer"))
#5. Chronic Pain
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Chron_pain,"Chronic Pain"))
#6. Diabetes
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Diabetes,"Diabetes"))
#7. Heart Attack
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Hrt_atk,"Heart Attack"))
#8. Heart Disease
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Hrt_dis,"Heart Disease"))
#9. High Cholesterol
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$High_chol,"High Cholesterol"))
#10. Hypertension
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$High_bld_press,"Hypertension"))
#11. Kidney Disease
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Kid_dis,"Kidney Disease"))
#12. Liver Disease
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Liv_dis,"Liver Disease"))
#13. Migrane
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Migrane,"Migrane"))
#14. MS
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$MS,"MS"))
#15. Osteoporosis
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Osteoporosis,"Osteoporosis"))
#15. Obesiety
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Obesity,"Obesity"))
#16. Rheumatoid Arthritis
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Rhum_arth,"RA"))
#17. Stroke
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$Stroke,"Stroke"))
# ### Mental Health Conditions
#18. Alcohol Use Disorder
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$AUD_Current,"AUD"))
#19. Drug Use Disorder
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$DUD_Current,"DUD"))
#20. Major Depressive Disorder
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$MDD_Current,"MDD"))
#22 Posttraumatic Stress Disorder
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$PTSD_Current,"PTSD"))
#23 Generalized Anxiety Disorder
Conditions_chi<-rbind(Conditions_chi,Condition_eval(thesis_NHRVS$GAD_Current,"GAD"))
```

Create a variable which selects significant health conditions to be used in the multivaraible regression model
```{r}
Conditions_X_use <- Conditions_chi |>
  mutate(
    p = as.numeric(p),
    sig = ifelse(
      as.numeric(Conditions_chi$p) < 0.05, 1, 0)
  )|>
  filter(
    sig == 1
  )

Conditions_X_use
```


```{r,include=FALSE}
# 
# #1. run model 1
#   df <- glm(Ex_rec  ~  Age + College + White_Race  + Income_60k_plus + Combat_Veteran + 
#                            TOTAL_TRAUMAS + BMI, data = thesis_NHRVS,family="binomial")
#   
# #2. summary of the model
#   df_summary <- summary(df)
#   df_sum <- tidy(df) 
# #4 Coefficients 
#   coefs_df <- abs(coef(df))
# #5. Odds ratio
#   OR_df <- exp(coef(df))
# #6. OR 95% CI
#   CI_df <- data.frame(round(exp(confint(df)),2))
# #7. P value function
#   p_val1<- cbind(df_sum$term ,df_sum$p.value)
#   adj.p <- FDR(pvalues = p_val1)
#   ADJ.p.values <- data.frame(rbind(adj.p$exclude, adj.p$select))
#   ADJ.p.values
# 
# #### Part 2. Make the table and export   
#   
# #1. Create a data frame
# tab_df <-  data.frame(cbind(
#   variable = df_sum$term[2:length(df_sum$term)],
#   Beta = coefs_df[2:length(df_sum$term)],
#   Wald = round(wald,2),
#   OR = OR_df[2:length(OR_df)],
#   CI = paste0("[",CI_df[2:length(OR_df),1], ",", CI_df[2:length(OR_df),2], "]"),
#   p = p_val1[2:length(length(p_val1[,2])),2]
# ))
# #2. left join adjusted p values
# #tab_df  <- left_join(tab_df, ADJ.p.values,by = join_by(p == p.value))
# 
# #3. 
# tab_tab <- data.frame(cbind(
#   variable = tab_df$variable,
#   Beta = tab_df$Beta,
#   Wald = tab_df$Wald,
#   OR = tab_df$OR,
#   CI = tab_df$CI,
#   p = tab_df$p
# ))
# #round the numbers
# tab_tab$Beta = round(as.numeric(tab_tab$Beta),2)
# tab_tab$Wald = round(as.numeric(tab_tab$Wald),2)
# tab_tab$OR = round(as.numeric(tab_tab$OR),2)
# tab_tab$p = tab_tab$p = round(as.numeric(tab_tab$p),4)
# 
# tab_tab[1,1] = string
# 
# output <- tab_tab[1,]
#   
#   return(output)
# }


```


For fun, Lets run some regressions with each condition seperately
```{r}
# Multivariate Logistic Multinomial Regression Function
# 
# Condition_eval_Reg<-function(Data,condition,string){
# 
# #1. run model 1
#   df <- glm(Ex_rec  ~ condition + Age + College + White_Race  + Income_60k_plus + Combat_Veteran + 
#                            TOTAL_TRAUMAS, data = Data,family="binomial")
#   
# #2. summary of the model
#   df_summary <- summary(df)
#   df_sum <- tidy(df) 
# #4 Coefficients 
#   coefs_df <- abs(coef(df))
# #5. Odds ratio
#   OR_df <- exp(coef(df))
# #6. OR 95% CI
#   CI_df <- data.frame(round(exp(confint(df)),2))
# #7. P value function
#   p_val1<- cbind(df_sum$term ,df_sum$p.value)
#   adj.p <- FDR(pvalues = p_val1)
#   ADJ.p.values <- data.frame(rbind(adj.p$exclude, adj.p$select))
#   ADJ.p.values
# 
# #### Part 2. Make the table and export   
#   
# #1. Create a data frame
# tab_df <-  data.frame(cbind(
#   variable = df_sum$term[2:length(df_sum$term)],
#   Beta = coefs_df[2:length(df_sum$term)],
#   Wald = round(wald,2),
#   OR = OR_df[2:length(OR_df)],
#   CI = paste0("[",CI_df[2:length(OR_df),1], ", ", CI_df[2:length(OR_df),2], "]"),
#   p = p_val1[2:length(length(p_val1[,2])),2]
# ))
# #2. left join adjusted p values
# #tab_df  <- left_join(tab_df, ADJ.p.values,by = join_by(p == p.value))
# 
# #3. 
# tab_tab <- data.frame(cbind(
#   variable = tab_df$variable,
#   Beta = tab_df$Beta,
#   Wald = tab_df$Wald,
#   OR = tab_df$OR,
#   CI = tab_df$CI,
#   p = tab_df$p
# ))
# #round the numbers
# tab_tab$Beta = round(as.numeric(tab_tab$Beta),2)
# tab_tab$Wald = round(as.numeric(tab_tab$Wald),2)
# tab_tab$OR = round(as.numeric(tab_tab$OR),2)
# tab_tab$p = tab_tab$p = round(as.numeric(tab_tab$p),4)
# 
# tab_tab[1,1] = string
# 
# output <- tab_tab[1,]
#   
#   return(output)
# }
#Its done!
```


```{r,include=FALS}
# ### Physical Health Conditions 
# # Conditions_reg = 0
# 
# #2. Arthritis
# Conditions_reg<-data.frame(Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Arthritis,"Arthritis"))
# #3. Asthma
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Athsma,"Athsma"))
# #4. Cancer
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Cancer,"Cancer"))
# #5. Chronic Pain
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Chron_pain,"Chronic Pain"))
# #6. Diabetes
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Diabetes,"Diabetes"))
# #7. Heart Attack
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Hrt_atk,"Heart Attack"))
# #8. Heart Disease
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Hrt_dis,"Heart Disease"))
# #9. High Cholesterol
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$High_chol,"High Cholesterol"))
# #10. Hypertension
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$High_bld_press,"Hypertension"))
# #11. Kidney Disease
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Kid_dis,"Kidney Disease"))
# #12. Liver Disease
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Liv_dis,"Liver Disease"))
# #13. Migrane
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Migrane,"Migrane"))
# #14. MS
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$MS,"MS"))
# #15. Osteoporosis
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Osteoporosis,"Osteoporosis"))
# #15.2 Obesity
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS$Obesity,"Obesity"))
# #16. Rheumatoid Arthritis
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Rhum_arth,"RA"))
# #17. Stroke
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$Stroke,"Stroke"))
# ### Mental Health Conditions
# #18. Alcohol Use Disorder
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$AUD_Current,"AUD"))
# #19. Drug Use Disorder
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$DUD_Current,"DUD"))
# #20. Major Depressive Disorder 
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$MDD_Current,"MDD"))
# #22 Posttraumatic Stress Disorder
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$PTSD_Current,"PTSD"))
# #23 Generalized Anxiety Disorder
# Conditions_reg<-rbind(Conditions_reg,Condition_eval_Reg(thesis_NHRVS,thesis_NHRVS$GAD_Current,"GAD"))
```

```{r}
# Conditions_R_use <- Conditions_reg |>
#   mutate(
#     signifcant = ifelse(
#       as.numeric(p) < 0.05, 1, 0)
#     ) |>
#   filter(
#     signifcant == 1
#   )
# 
# Conditions_R_use
```



### Block 2: Physical Health Conditions
Block to is idential to block one with the addition of the MCS and PCS to the regression model. We are running two different regession models (i.e., one with the MCS and one with the PCS) so you can see that below. 
```{r,warning=FALSE,message=FALSE,results='hide'}
### Part 1 Physical health conditions for table
#1. Run the models
PHC_Reg<-glm(Ex_rec~
             #Covariates
             Age + College + White_Race  +
             Income_60k_plus + Combat_Veteran + 
             TOTAL_TRAUMAS +
             #Physical Health Conditions
             Athsma + Chron_pain + Diabetes+ Hrt_atk + 
             Hrt_dis + High_chol + High_bld_press + Osteoporosis + Obesity + Stroke,
             #Mental Health conditions
             # AUD_Current + DUD_Current + MDD_Current + PTSD_Current + GAD_Current,
             # Data
             data =thesis_NHRVS,
             # Specify type of regression
             family="binomial",weights = weight)


summary(PHC_Reg)
PHC_Reg_sum <- tidy(PHC_Reg) 

#2. Coefficients 
  coefs_PHC_Reg <- abs(coef(PHC_Reg))
  coefs_PHC_Reg
#3. Odds ratio
  OR_PHC_Reg <- exp(coef(PHC_Reg)[8:length(coefs_PHC_Reg)])

#4. OR 95% CI
  CI_PHC_Reg <- data.frame(round(exp(confint(PHC_Reg)[8:length(coefs_PHC_Reg),]),2))

#5. P values 
  p_val1<- cbind(PHC_Reg_sum$term[8:length(coefs_PHC_Reg)], 
                 PHC_Reg_sum$p.value[8:length(coefs_PHC_Reg)])
    adj.p <- FDR(pvalues = p_val1)
    ADJ.p.values <- data.frame(rbind(adj.p$exclude, adj.p$select))
    ADJ.p.values
    
#6. R^2 for model
  R2_PHC_Reg <- performance::r2(PHC_Reg) 
  block_2_R2 = R2_PHC_Reg[[1]] - R2_Cov_Reg[[1]]
#wald
  library(aod) # Wald test
  PHC_wald<- wald.test(b = coef(PHC_Reg),Sigma = vcov(PHC_Reg),Terms= 2:length(coefs_PHC_Reg))
  PHC_wald$result$chi2[1]
  wald <- wald.test(b = coef(PHC_Reg),Sigma = vcov(PHC_Reg),Terms=8)$result$chi2[1]
  for(i in 9:length(coefs_PHC_Reg)){
      wald <- append(wald, wald.test(b = coef(PHC_Reg),Sigma = vcov(PHC_Reg),Terms=i)$result$chi2[1])
  }
#### Part 2. Make the table and export 

#1. Create data frame
PHC_Reg_df <-  data.frame(cbind(
  variable = PHC_Reg_sum$term[8:length(PHC_Reg_sum$term)],
  Beta = coefs_PHC_Reg[8:length(coefs_PHC_Reg)],
  Wald = round(wald,2),
  OR = OR_PHC_Reg,
  CI = paste0("[",CI_PHC_Reg[,1], ", ", CI_PHC_Reg[,2], "]"),
  p = p_val1[,2]
))

PHC_Reg_df  <- left_join(PHC_Reg_df, ADJ.p.values,by = join_by(p == p.value))
PHC_Reg_tab <- data.frame(cbind(
  variable = PHC_Reg_df$variable,
  Beta = PHC_Reg_df$Beta,
  Wald = PHC_Reg_df$Wald,
  OR = PHC_Reg_df$OR,
  CI = PHC_Reg_df$CI,
  # p = PHC_Reg_df$p
  p = PHC_Reg_df$p.adjusted
))

PHC_Reg_df 

PHC_Reg_tab$Beta = round(as.numeric(PHC_Reg_tab$Beta),2)
PHC_Reg_tab$Wald = round(as.numeric(PHC_Reg_tab$Wald),2)
PHC_Reg_tab$OR = round(as.numeric(PHC_Reg_tab$OR),2)
PHC_Reg_tab$p = ifelse(as.numeric(PHC_Reg_df$p) < 0.001, "< 0.001",
  round(as.numeric(PHC_Reg_df$p),3))

#2. create the row for the R2
  paste("Block 2 R^2 =", round((R2_PHC_Reg[[1]]*100),3),"%")
  variable = c(
    "Block 2 - Physical Health Conditions",
    paste0("X^2=", round(PHC_wald$result$chi2[1],2),",p<0.001"),
    paste0("R^2 change=", round((block_2_R2[[1]]),3))  
  )

  R2TAB<-data.frame(cbind(
                      variable,Beta=NA,Wald=NA, OR =NA, CI=NA, p=NA))

#3. Bind the stuff together
  PHC_Reg_tab <- rbind(R2TAB, PHC_Reg_tab)
  Full_OR_tab <- rbind(cov_OR_tab,PHC_Reg_tab)

#4. Export
  # write_csv(PHC_Reg_tab,"~/Desktop/Coding/data/PHC_Reg_tab.csv")
  # write_csv(Full_OR_tab, "~/Desktop/Coding/data/EX_Full_OR_tab.csv")
  
  PHC_Reg_tab

```
```{r}
  knitr::kable(Full_OR_tab) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

block 3 - mental health conditions
```{r}
MHC_Reg<-glm(Ex_rec~
             #Covariates
             Age + College + White_Race  +
             Income_60k_plus + Combat_Veteran + 
             TOTAL_TRAUMAS + 
             #Physical Health Conditions
             Athsma + Chron_pain + Diabetes+ Hrt_atk + 
             Hrt_dis + High_chol + High_bld_press + Osteoporosis + Obesity + Stroke +
             #Mental Health conditions
             AUD_Current + DUD_Current + GAD_Current + MDD_Current + PTSD_Current,
             # Data
             data =thesis_NHRVS,
             # Specify type of regression
             family="binomial",weights = weight)


summary(MHC_Reg)
MHC_Reg_sum <- tidy(MHC_Reg) 

#2. Coefficients 
  coefs_MHC_Reg <- abs(coef(MHC_Reg))
  coefs_MHC_Reg
#3. Odds ratio
  OR_MHC_Reg <- exp(coef(MHC_Reg)[18:length(coefs_MHC_Reg)])

#4. OR 95% CI
  CI_MHC_Reg <- data.frame(round(exp(confint(MHC_Reg)[18:length(coefs_MHC_Reg),]),2))

#5. P values 
  p_val1<- cbind(MHC_Reg_sum$term[18:length(coefs_MHC_Reg)], 
                 MHC_Reg_sum$p.value[18:length(coefs_MHC_Reg)])
    adj.p <- FDR(pvalues = p_val1)
    ADJ.p.values <- data.frame(rbind(adj.p$exclude, adj.p$select))
    ADJ.p.values
    
#6. R^2 for model
  R2_MHC_Reg <- performance::r2(MHC_Reg)
  Block3_R2 = R2_MHC_Reg[[1]] - R2_PHC_Reg[[1]]

#wald
  library(aod) # Wald test
  MHC_wald<- wald.test(b = coef(MHC_Reg),Sigma = vcov(MHC_Reg),Terms= 2:length(coefs_MHC_Reg))
  MHC_wald$result$chi2[1]
  wald <- wald.test(b = coef(MHC_Reg),Sigma = vcov(MHC_Reg),Terms=18)$result$chi2[1]
  for(i in 19:length(coefs_MHC_Reg)){
      wald <- append(wald, wald.test(b = coef(MHC_Reg),Sigma = vcov(MHC_Reg),Terms=i)$result$chi2[1])
  }
  MHC_wald
#### Part 2. Make the table and export 

#1. Create data frame
MHC_Reg_df <-  data.frame(cbind(
  variable = MHC_Reg_sum$term[18:length(MHC_Reg_sum$term)],
  Beta = coefs_MHC_Reg[18:length(coefs_MHC_Reg)],
  Wald = round(wald,2),
  OR = OR_MHC_Reg,
  CI = paste0("[",CI_MHC_Reg[,1], ", ", CI_MHC_Reg[,2], "]"),
  p = p_val1[,2]
))

MHC_Reg_df  <- left_join(MHC_Reg_df, ADJ.p.values,by = join_by(p == p.value))
MHC_Reg_tab <- data.frame(cbind(
  variable = MHC_Reg_df$variable,
  Beta = MHC_Reg_df$Beta,
  Wald = MHC_Reg_df$Wald,
  OR = MHC_Reg_df$OR,
  CI = MHC_Reg_df$CI,
  p = MHC_Reg_df$p
  # p = MHC_Reg_df$p.adjusted
))

MHC_Reg_df 

MHC_Reg_tab$Beta = round(as.numeric(MHC_Reg_tab$Beta),2)
MHC_Reg_tab$Wald = round(as.numeric(MHC_Reg_tab$Wald),2)
MHC_Reg_tab$OR = round(as.numeric(MHC_Reg_tab$OR),2)
MHC_Reg_tab$p = ifelse(as.numeric(MHC_Reg_df$p) < 0.001, "< 0.001",
  round(as.numeric(MHC_Reg_df$p),3))

#2. create the row for the R2
  variable = c(
    "Block 3 - Mental Health Conditions",
    paste0("X^2=", round(MHC_wald$result$chi2[1],2),",p<0.001"),
    paste0("R^2 change=", round((Block3_R2[[1]]),3))  
  )

  R2TAB<-data.frame(cbind(
                      variable,Beta=NA,Wald=NA, OR =NA, CI=NA, p=NA))

#3. Bind the stuff together
  MHC_Reg_tab <- rbind(R2TAB, MHC_Reg_tab)
  Full_OR_tab <- rbind(Full_OR_tab,MHC_Reg_tab)

#4. Export
  # write_csv(MHC_Reg_tab,"~/Desktop/Coding/data/MHC_Reg_tab.csv")
  # write_csv(Full_OR_tab, "~/Desktop/Coding/data/EX_Full_OR_tab.csv")
  
  MHC_Reg_tab
  Full_OR_tab
```


Prepare for table

```{r}
#create FP df
fp_df <- data.frame(rbind(
  #Block 1
  NA,NA,NA,NA,
  arrange(cov_OR_df,desc(OR)),
  #Block 2
  NA,NA,NA,NA,
  arrange(PHC_Reg_df,desc(OR)),
  #Block 3
  NA,NA,NA,NA,
  arrange(MHC_Reg_df,desc(OR)),
  #Top row
  NA
))

fp_df
```


```{r}
fp_df <- mutate(fp_df,
    sig = ifelse(is.na(p.adjusted), NA, 
          ifelse(p.adjusted<= 0.05, 16,1)),
    Beta = round(as.numeric(fp_df$Beta),2),
    OR =  round(as.numeric(fp_df$OR),2),
    p_fig = ifelse(
      is.na(p.adjusted), NA,
      ifelse(p.adjusted < 0.001, "<0.001", 
             round(as.numeric(p.adjusted),3))),
    order = 0
    )

#make CI variables df
OR_CI <-data.frame(rbind(
    NA,NA,NA,NA,
    CI_Cov_Reg[2:length(CI_Cov_Reg$X2.5..),],
    NA,NA,NA,NA,
    CI_PHC_Reg,
    NA,NA,NA,NA,
    CI_MHC_Reg,
    NA
))
OR_CI$variables = rownames(OR_CI)

#left join CI based upon varaible names
fp_df <- left_join(fp_df,OR_CI, by = join_by(variable == variables))
colnames(fp_df)[11:12] <- c("OR_low","OR_high")

#create OR label for FP
fp_df <- mutate(fp_df,
    label = 
      #NAs      
      ifelse(is.na(OR) |is.na(CI),NA,
      #p <.05      
      ifelse(p.adjusted <= 0.05 & p.adjusted >= 0.01,
                   paste0(OR," [",OR_low,"-",OR_high,"]*"),
      #p<.01
      ifelse(p.adjusted < 0.01 & p.adjusted >= 0.001,
                   paste0(OR," [",OR_low,"-",OR_high,"]**"),
      #p<.001
      ifelse(p.adjusted < 0.001,
                   paste0(OR," [",OR_low,"-",OR_high,"]***"),
      # else (i.e., p > .05)
             paste0(OR," [",OR_low,"-",OR_high,"]")
      )))))


#assign variable names
fp_df$variable <- c(
    "Block 1",
    "Covariates",
    paste0("X^2=", round(cov_wald$result$chi2[1],2),",p<0.001"),
    paste0("R^2=", round((R2_Cov_Reg[[1]]),3)),
    "Some College",
    "Income ≥ 60k",
    "Combat Veteran",
    "White",
    "# of Traumas",
    "Age", 
    "Block 2",
    "Physical Health", 
    paste0("X^2=", round(PHC_wald$result$chi2[1],2),",p<0.001"),
    paste0("R^2 change=", round((block_2_R2[[1]]),3)),
    "Hypertension",   
    "Heart Disease",
    "Chronic Pain",
    "High Cholesterol",
    "Osteoporosis",
    "Asthma",  
    "Heart Attack",
    "Stroke", 
    "Obesity",
    "Diabetes", 
    "Block 3",
    "Mental Health",
    paste0("X^2=", round(MHC_wald$result$chi2[1],2),",p<0.001"),
    paste0("R^2 change=", round((Block3_R2[[1]]),3)),
    "Probable Current GAD",
    "Probable Current PTSD",
    "Probable Current AUD",
    "Probable Current DUD",
    "Probable Current MDD",
    "Variable")


# assign labels to top row and assign the order of varaibles
fp_df[34,2] = "Beta"
fp_df[34,3] = "Wald"
fp_df[34,13] = "OR [95% CI]"
fp_df[34,9] = "Adjusted p"
fp_df$order = c(seq(2,34,1),1)
#Final df for FP
fp_df
```


FP for logistic Regressions
```{r}
#Create order varaible in dataset to keep it the same as the regression

# FP_EX <- read_csv("~/Downloads/FP.min.dep")

#rename the variables for the figure
# install.packages("magrittr")
# library(magrittr)

EX_FP <- 
  fp_df |>
  ggplot(aes(y = reorder(variable, -order), color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape= 16,
               # ifelse(FP_dep$p.adjusted <= 0.05, 
               #                        16, # colored ones for significant varaibles
               #                        1), # uncolored ones for insignificant varaibles
             size=4,show.legend = FALSE) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = 1, show.legend = FALSE) +
  # geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.6, show.legend = FALSE) +
  scale_color_manual(values = c("black","black"))+
  #change x axis name
  labs(
    x="Odds Ratio",
    # title = "    Odds of Meeting Physical Activity Guidelines",
    subtitle ="Odds of Meeting Physical Activity Guidelines") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,length(fp_df$variable))) +
  #add a line at 1 for reference 
  geom_vline(xintercept = 1,linetype="dashed",alpha = .50) + 
  #add anotations to help suggests what each side means.
  annotate("text", x = .6, y = length(fp_df$variable) -1 , label = "Less Likely", size= 4) +
  annotate("text", x = 1.4, y = length(fp_df$variable) -1, label = "More Likely",size= 4) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

EX_text <- 
  fp_df |>
  ggplot(aes(y = reorder(variable, -order))) +
  geom_text(aes(x = 0, label = variable), hjust = 0, 
        fontface = ifelse(fp_df$variable == "Variable" |
                          fp_df$variable == "Block 1"  |
                          fp_df$variable == "Block 2"  |
                          fp_df$variable == "Block 3", "bold","plain")) +
  geom_text(aes(x = 1.1, label = Beta),
        hjust = 0,
        fontface = ifelse(fp_df$Beta == "Beta", "bold","plain")) + 
  geom_text(aes(x = 1.5, label = Wald),
        hjust = 0,
        fontface = ifelse(fp_df$Wald == "Wald", "bold","plain")) +
  geom_text(aes(x = 1.9, label = label),
        hjust = 0,
        fontface = ifelse(fp_df$label == "OR [95% CI]", "bold","plain")) +
  theme_void() +     
  coord_cartesian(ylim = c(1,length(fp_df$variable)), xlim = c(0, 4))

library("patchwork")

layout <- c(
  patchwork::area(t = 0, l = 0, b = 30, r = 25),
  patchwork::area(t = 0, l = 17, b = 30, r = 26)
)

EX_text + EX_FP + plot_layout(design = layout)
```


<!-- ## Importance of variables -->
<!-- https://journals-sagepub-com.ezproxy.uky.edu/doi/abs/10.1177/1094428109341993?journalCode=orma -->

<!-- Select data needed for analysis -->
<!-- ```{r} -->
<!-- RIA_Vars<-fp_df |> -->
<!--   # arrange(p.adjusted) -->
<!--   filter(p.adjusted <0.05) -->
<!-- RIA_Vars -->
<!-- ``` -->


<!-- ```{r} -->
<!-- mydata <- thesis_NHRVS |> -->
<!--     mutate(Obesity = ifelse(is.na(BMI), NA, -->
<!--       ifelse(BMI >=30,1,0)) -->
<!--     ) |> -->
<!--   #Select all of the variables needed for the analysis -->
<!--   dplyr::select( -->
<!--     #IV -->
<!--       Ex_rec, -->
<!--     #Covariates -->
<!--        Age,College, -->
<!--        Income_60k_plus, -->
<!--     #Physical Health Conditions -->
<!--        Athsma, Diabetes, Obesity, -->
<!--        # Hrt_atk, Hrt_dis,  -->
<!--     #Mental Health conditions -->
<!--       DUD_Current, GAD_Current, MDD_Current,  -->
<!--   )|> -->
<!--     # Convert all of the varaibles to numeric -->
<!--     mutate( -->
<!--       Ex_rec = as.numeric(Ex_rec), -->
<!--       Age = as.numeric(Age), -->
<!--       College = as.numeric(College), -->
<!--       Income_60k_plus = as.numeric(Income_60k_plus), -->
<!--       Obesity = as.numeric(Obesity), -->
<!--       Athsma = as.numeric(Athsma), -->
<!--       Diabetes = as.numeric(Diabetes), -->
<!--       DUD_Current = as.numeric(DUD_Current),  -->
<!--       GAD_Current = as.numeric(GAD_Current), -->
<!--       MDD_Current = as.numeric(MDD_Current),  -->

<!--     ) -->

<!-- mydata <- na.omit(mydata) -->
<!-- ``` -->

<!-- Functions for bootstrapping -->
<!-- ```{r} -->
<!-- logRegress<-function(mydata){ -->

<!-- numVar<-NCOL(mydata) -->
<!-- Variables<-names(mydata)[2:numVar] -->
<!-- Y<-mydata[,1] -->
<!-- data.preds<-mydata[,2:length(mydata[1,])] -->
<!-- X<-scale(data.preds) -->


<!-- str(X) -->

<!-- X.svd<-svd(X) -->
<!-- Q<-X.svd$v -->
<!-- P<-X.svd$u -->
<!-- Z<-P%*%t(Q) -->

<!-- Z.stand<-scale(Z) -->

<!-- Lambda<-solve(t(Z.stand)%*%Z.stand)%*%t(Z.stand)%*%X #Obtaining Lambda from equation 7 from Johnson (2000) pg 8 -->

<!-- logrfit<-glm(as.factor(Y$Ex_rec)~Z.stand,family=binomial) -->
<!-- summary(logrfit) -->
<!-- unstCoefs<-coef(logrfit) -->
<!-- b<-unstCoefs[2:length(unstCoefs)] -->
<!-- LpredY<-predict(logrfit,newdata=mydata,type="response") -->
<!-- lYhat<-log(LpredY/(1-LpredY))#Creating logit-Y-hat -->
<!-- stdlYhat<-sd(lYhat)#Getting stdev of logit-Y-hat -->
<!-- getting.Rsq<-lm(LpredY~as.factor(Y$Ex_rec))#Getting R-sq -->
<!-- Rsq<-summary(getting.Rsq)$r.squared -->
<!-- beta<-b*((sqrt(Rsq))/stdlYhat)#Computing standardized logistic regression coefficients -->

<!-- epsilon<-Lambda^2%*%beta^2 -->
<!-- R.sq<<-sum(epsilon) -->
<!-- PropWeights<-(epsilon/R.sq) -->
<!-- result <- data.frame(Variables, Raw.RelWeight=epsilon, Rescaled.RelWeight=PropWeights) -->
<!-- return(result) -->
<!-- } -->

<!-- logBootstrap<-function(mydata, indices){ -->
<!-- mydata<-mydata[indices,] -->
<!-- logWeights<-logRegress(mydata) -->
<!-- return(logWeights$Raw.RelWeight) -->
<!-- } -->

<!-- logBootstrap_adj<-function(mydata, indices){ -->
<!-- mydata<-mydata[indices,] -->
<!-- logWeights<-logRegress(mydata) -->
<!-- return(logWeights$Rescaled.RelWeigh) -->
<!-- } -->

<!-- logBootrand<-function(mydata, indices){ -->
<!-- mydata<-mydata[indices,] -->
<!-- logRWeights<-logRegress(mydata) -->
<!-- logReps<-logRWeights$Raw.RelWeight -->
<!-- randWeight<-logReps[length(logReps)] -->
<!-- randStat<-logReps[-(length(logReps))]-randWeight -->
<!-- return(randStat) -->
<!-- } -->

<!-- #bootstrapping -->
<!-- #install.packages("boot") -->

<!-- mybootci<-function(x){ -->
<!-- boot.ci(logBoot,conf=0.95, type="bca", index=x) -->
<!-- } -->

<!-- runBoot<-function(num){ -->
<!-- INDEX<-1:num -->
<!-- test<-lapply(INDEX, FUN=mybootci) -->
<!-- test -->
<!-- test2<-t(sapply(test,'[[',i=4)) -->
<!-- return(test2) -->
<!-- # CIresult<<-data.frame(Variables = coln, CI.Lower.Bound=test2[,4],CI.Upper.Bound=test2[,5]) -->
<!-- } -->

<!-- myRbootci<-function(x){ -->
<!-- boot.ci(logRBoot,conf=0.95,type="bca",index=x) -->
<!-- } -->

<!-- runRBoot<-function(num){ -->
<!-- INDEX<-1:num -->
<!-- test<-lapply(INDEX,FUN=myRbootci) -->
<!-- test2<-t(sapply(test,'[[',i=4)) -->
<!-- CIresult<<-data.frame(Labels,CI.Lower.Bound=test2[,4],CI.Upper.Bound=test2[,5]) -->
<!-- } -->
<!-- ``` -->


<!-- ```{r, results='hide'} -->
<!-- #1.1 Run function -->
<!-- result <- logRegress(mydata) -->

<!-- #1.2 save results from function -->
<!-- RW.Results<-result -->
<!-- RSQ.o<-R.sq -->

<!-- RW.Results <- result |> -->
<!--   arrange(-Rescaled.RelWeight) |> -->
<!--   mutate(Rescaled.RelWeight.percent = round((Rescaled.RelWeight*100),2), -->
<!--          Raw.percent = round(Raw.RelWeight*100,4) -->
<!--   ) -->
<!-- # write_csv(RW.Results,"~/Downloads/RW.Results") -->

<!-- #1.3 display results of relative weight analysis -->
<!-- RW.Results -->
<!-- ``` -->


<!-- ```{r, results='hide'} -->
<!-- #2 Use bootstrapping functions to obtain CI's for raw and rescaled weights -->

<!-- #2.1 the boot function calls the logBootstrap and logBootstrap_adj function, which just pulls out the raw.relWeight and rescaled.relWeight at a given index -->

<!-- mydata_B3 <- mydata -->

<!-- #2.3 Set seed -->
<!-- set.seed(1995) -->

<!-- #2.4 bootstrap for raw weights CI -->
<!-- logBoot_B3 <-boot(mydata_B3, # Data -->
<!--               logBootstrap, # Statistic -->
<!--               10000) # R / number of times -->

<!--  <- tidy(logBoot_B3) -->

<!-- # CI.Results_tidy <- tidy(logBoot_B3,conf.int=TRUE) -->
<!-- numVar = NCOL(mydata_B3) -->
<!-- mydata <- mydata -->
<!-- logBoot <-logBoot_B3 -->
<!-- # logBoot<-boot(mydata_B3, logBootstrap, 10000) -->

<!-- ?boot.ci() -->

<!-- logci<-boot.ci(logBoot,conf=0.95, type="bca") -->
<!-- numVar = length(mydata) -->
<!-- test2 <- runBoot(length(mydata[,2:numVar])) -->
<!-- #df with CI -->
<!-- CI.Result<<-data.frame(Variables=colnames(mydata[2:10]), CI.Lower.Bound=test2[,4],CI.Upper.Bound=test2[,5]) -->
<!-- CI.Result -->
<!-- write_csv(CI.Result, "/Users/troyh/Downloads/CI.Result") -->
<!-- ``` -->


<!-- ```{r, results='hide'} -->
<!-- #rescaled CI -->
<!-- logBoot_adj <-boot(mydata_B3, # Data -->
<!--               logBootstrap_adj, # Statistic -->
<!--               10000) # R / number of times -->

<!-- numVar = NCOL(mydata_B3) -->
<!-- mydata <- mydata -->
<!-- logBoot <-logBoot_adj -->
<!-- # logBoot<-boot(mydata_B3, logBootstrap, 10000) -->
<!-- logci<-boot.ci(logBoot,conf=0.95, type="bca") -->
<!-- numVar = length(mydata) -->
<!-- test2 <- runBoot(length(mydata[,2:numVar])) -->
<!-- test2 -->

<!-- test -->




<!-- #df with CI -->
<!-- CI.Result.res<<-data.frame(Variables=colnames(mydata[2:10]), CI.Lower.Bound=test2[,4],CI.Upper.Bound=test2[,5]) -->
<!-- CI.Result.res -->
<!-- write_csv(CI.Result.res, "/Users/troyh/Downloads/CI.Result") -->
<!-- ``` -->


<!-- ```{r, results='hide'} -->
<!-- #Bootstrapped Confidence interval tests of Significance -->
<!-- #Please be patient -- This can take a few minutes to run -->
<!-- randVar<-rnorm(length(mydata[,1]),0,1) -->
<!-- randData<-cbind(mydata,randVar) -->
<!-- logRBoot<-boot(randData,logBootrand, 10000) -->
<!-- logRci<-boot.ci(logRBoot,conf=0.95, type="bca") -->
<!-- runRBoot(length(randData[,2:(numVar-1)])) -->
<!-- CI.Significance<-CIresult -->

<!-- ``` -->


<!-- ```{r, results='hide'} -->
<!-- #display results -->

<!-- #Rsq.O - logistic analog to Rsq -->
<!-- RSQ.o -->

<!-- #The Raw and Rescaled Weights -->
<!-- RW.Results -->

<!-- #BCa Confidence Intervals around the raw weights -->
<!-- colnames(CI.Result) <- paste0(colnames(CI.Result),"_Raw") -->
<!-- CI.Result -->

<!-- #Confidence intervals -->
<!-- colnames(CI.Result.res) <- paste0(colnames(CI.Result.res),"_Rescale") -->
<!-- CI.Result.res -->
<!-- #If Zero is not included, Weight is Significant -->

<!-- #left join bootstraped results to RW.Results df -->
<!-- RW.Results -->
<!-- RW.Results <- left_join(RW.Results,CI.Result, by = join_by(Variables == Variables_Raw)) -->
<!-- RW.Results <- left_join(RW.Results,CI.Result.res, by = join_by(Variables == Variables_Rescale)) -->

<!-- #final DF -->
<!-- RW.Results -->
<!-- ``` -->

<!-- bar plots of results -->
<!-- ```{r, results='hide'} -->
<!-- #create new df with CIs and values as % -->
<!-- wt_df <- RW.Results |> -->
<!--   mutate( -->
<!--   raw.CI = paste0("[", round(CI.Lower.Bound_Raw*100,2), ", ",  -->
<!--                   round(CI.Upper.Bound_Raw*100,2), "]"), -->
<!--   raw.CI.low = round(CI.Lower.Bound_Raw*100,2), -->
<!--   raw.CI.high = round(CI.Upper.Bound_Raw*100,2), -->
<!--   res.CI = paste0("[", round(CI.Lower.Bound_Rescale*100,2), ", ",  -->
<!--                   round(CI.Upper.Bound_Rescale*100,2), "]"), -->
<!--   res.CI.low = round(CI.Lower.Bound_Rescale*100,2), -->
<!--   res.CI.high = round(CI.Upper.Bound_Rescale*100,2), -->
<!--   order = NA, -->
<!--   Raw.wt.text = round(Raw.percent,2), -->
<!--   Res.wt.text = round(Rescaled.RelWeight.percent,2), -->
<!--   raw.weight = (CI.Lower.Bound_Raw + CI.Upper.Bound_Raw)/2, -->
<!--   res.weight = (CI.Lower.Bound_Rescale*100 + CI.Upper.Bound_Rescale*100)/2, -->
<!--   ) -->
<!-- wt_df -->
<!-- ``` -->


<!-- ```{r, results='hide'} -->
<!-- #assign variables and put them at the top -->
<!--   wt_df[10,]   = NA   -->
<!--   wt_df[10,1]  = "Variable" -->
<!--   wt_df[10,10] = "95% CI" -->
<!--   wt_df[10,13] = "95% CI" -->
<!--   wt_df[10,17]  = "R2o (%)"   -->
<!--   wt_df[10,18]  = "Rescaled R2o (%)"  -->

<!--   wt_df$order  = c(seq(2,10,1),1) -->
<!--   wt_df <- arrange(wt_df,order) -->

<!-- wt_df -->
<!-- write.csv() -->

<!-- ?reorder() -->
<!-- ``` -->

<!-- code -->
<!-- ```{r} -->
<!-- # # plot raw R^2 values w/ 95% CI -->
<!-- # R2_plot <-  -->
<!-- #   ggplot2::ggplot(wt_df, aes(x=reorder(Variables,-order),y=Raw.percent)) + -->
<!-- #   # geom_hline(yintercept = 1,linetype="dashed",alpha = .25) + -->
<!-- #   # geom_hline(yintercept = .5,linetype="dashed",alpha = .25) + -->
<!-- #   geom_bar(stat = "identity", color = "Black", width = .75, fill = "#91c3e6" ) + -->
<!-- #   geom_errorbar(aes(ymin=raw.CI.low, ymax=raw.CI.high,width =.3, show.legend = FALSE)) + -->
<!-- #   labs( -->
<!-- #     #title = "     Varaince Explained (%) Of Phsyical Activity by Predictors", -->
<!-- #     subtitle = "      Varaince Explained (%) Of Phsyical Activity by Predictors", -->
<!-- #   ) + -->
<!-- #   theme_classic() + -->
<!-- #   xlab('Variable')+ -->
<!-- #   ylab('R2o in physical activity (%)')+ -->
<!-- #   ylim(0,2.5)+ -->
<!-- #   coord_flip() + -->
<!-- #   theme(axis.line.y = element_blank(), -->
<!-- #         axis.ticks.y= element_blank(), -->
<!-- #         axis.text.y= element_blank(), -->
<!-- #         axis.title.y= element_blank()) -->
<!-- #  -->
<!-- # R2_plot -->
<!-- #  -->
<!-- # #plot table left of text -->
<!-- # wt_df$Variables = c("Variable","Obesity","Some College","Diabetes", "Age",  -->
<!-- #                     "Income ≥ 60k", "Asthma", "Probable Current MDD", -->
<!-- #                     "Probable Current GAD", "Probable Current DUD" -->
<!-- #                     ) -->
<!-- #  -->
<!-- #  -->
<!-- #  -->
<!-- # R2_text <-  -->
<!-- #   wt_df |> -->
<!-- #   ggplot(aes(y = reorder(Variables, -order))) + -->
<!-- #   geom_text(aes(x = 0, label = Variables), hjust = 0,  -->
<!-- #         fontface = ifelse(wt_df$Variables == "Variable", "bold","plain")) + -->
<!-- #   geom_text(aes(x = 1.2, label = Raw.wt.text), -->
<!-- #         hjust = 0, -->
<!-- #         fontface = ifelse(wt_df$Raw.wt.text == "R2o (%)", "bold","plain")) + -->
<!-- #   geom_text(aes(x = 1.7, label = raw.CI), -->
<!-- #         hjust = 0, -->
<!-- #         fontface = ifelse(wt_df$raw.CI == "95% CI", "bold","plain")) + -->
<!-- #   theme_void() +      -->
<!-- #   coord_cartesian(ylim = c(1,length(wt_df$Variables)), xlim = c(0, 4)) -->
<!-- #    -->
<!-- # library("patchwork") -->
<!-- #  -->
<!-- # layout <- c( -->
<!-- #   patchwork::area(t = 0, l = 0, b = 30, r = 30), -->
<!-- #   patchwork::area(t = 0, l = 18, b = 30, r = 35) -->
<!-- # ) -->
<!-- #  -->
<!-- # R2_text + R2_plot + plot_layout(design = layout) -->
<!-- #  -->

<!-- ``` -->

<!-- ### Part 5 barplots -->

<!-- Scaled weight Barplot  -->
<!-- ```{r, results='hide'} -->
<!-- # wt_plot <-  -->
<!--   ggplot2::ggplot(wt_df, aes(x=stats::reorder(Variables,-order),y=Rescaled.RelWeight.percent)) + -->
<!--   geom_bar(stat = "identity", color = "Black", width = .75, fill = "#91c3e6" )+ -->
<!--   geom_errorbar(aes(ymin=res.CI.low, ymax=res.CI.high,width =.3, show.legend = FALSE)) + -->
<!--   labs( -->
<!--     # title = "     Relative Weight (%) Of Predictors On Physical Activity", -->
<!--     subtitle ="Relative Weight (%) Of Predictors On Physical Activity"  -->
<!--       #"      RIA with 10000 bootstrapped confidence intervals" -->
<!--   ) + -->
<!--   theme_classic() + -->
<!--   xlab('Variable')+ -->
<!--   ylab('Weight (%) of variance (R2o) in physical activity')+ -->
<!--   ylim(0,50)+ -->
<!--   # geom_text(aes(label = wt_text), vjust =.5, hjust = -.1, color = "black")+ -->
<!--   coord_flip()  + -->
<!--     theme(axis.line.y = element_blank(), -->
<!--         axis.ticks.y= element_blank(), -->
<!--         axis.text.y= element_blank(), -->
<!--         axis.title.y= element_blank()) -->

<!-- wt_text <-  -->
<!--   wt_df |> -->
<!--   ggplot(aes(y = reorder(Variables, -order))) + -->
<!--   geom_text(aes(x = 0, label = Variables), hjust = 0,  -->
<!--         fontface = ifelse(wt_df$Variables == "Variable", "bold","plain")) + -->
<!--   geom_text(aes(x = 1.1, label = Res.wt.text), -->
<!--         hjust = 0, -->
<!--         fontface = ifelse(wt_df$Res.wt.text == "Scaled Weight (%)", "bold","plain")) + -->
<!--   geom_text(aes(x = 2, label = rescale.CI), -->
<!--         hjust = 0, -->
<!--         fontface = ifelse(wt_df$rescale.CI == "95% CI", "bold","plain")) + -->
<!--   theme_void() +      -->
<!--   coord_cartesian(ylim = c(1,length(wt_df$Variables)), xlim = c(0, 4)) -->

<!-- library("patchwork") -->

<!-- layout <- c( -->
<!--   patchwork::area(t = 0, l = 0, b = 30, r = 30), -->
<!--   patchwork::area(t = 0, l = 21, b = 30, r = 40) -->
<!-- ) -->

<!-- wt_text + wt_plot + plot_layout(design = layout) -->
<!-- ``` -->


<!-- ```{r, results='hide'} -->
<!-- wt_df <- RW.Results |> -->
<!--   mutate( -->
<!--   raw.CI = paste0("[", round(conf.low_Raw.CI*100,2), ", ",  -->
<!--                   round(conf.high_Raw.CI*100,2), "]"), -->
<!--   raw.CI.low = round(conf.low_Raw.CI*100,2), -->
<!--   raw.CI.high = round(conf.high_Raw.CI*100,2), -->
<!--   rescale.CI = paste0("[", round(conf.low_Rescale.CI*100,2), ", ",  -->
<!--                       round(conf.high_Rescale.CI*100,2), "]"), -->
<!--   rescale.CI.low = round(conf.low_Rescale.CI*100,2), -->
<!--   rescale.CI.high = round(conf.high_Rescale.CI*100,2), -->
<!--   order = NA, -->
<!--   Raw.wt.text = round(Raw.percent,2), -->
<!--   Res.wt.text = round(Rescaled.RelWeight.percent,2) -->
<!--   ) -->
<!-- ``` -->
















<!-- using varImp from {caret} we can examine the relative importance of each variable -->
<!-- ### Binary outcome -->
<!-- ```{r} -->
<!-- # library(caret) -->
<!-- # #https://topepo.github.io/caret/variable-importance.html -->
<!-- #  -->
<!-- # V <- varImp(MHC_Reg, Scale=TRUE) -->
<!-- #  -->
<!-- # V <- V |> -->
<!-- #   mutate( -->
<!-- #     wt_scaled = round((Overall/sum(Overall))*100,2), -->
<!-- #   variable =  -->
<!-- #     c("Age", "College", "White_Race", "Income_60k_plus", "Combat_Veteran",  -->
<!-- #       "TOTAL_TRAUMAS", "BMI", "Athsma", "Chron_pain", "Diabetes", "Hrt_atk",  -->
<!-- #       "Hrt_dis", -->
<!-- #       "High_chol", "High_bld_press", "Osteoporosis", "Stroke", "AUD_Current",  -->
<!-- #       "DUD_Current", "MDD_Current", "PTSD_Current","GAD_Current") -->
<!-- #   ) -->
<!-- #  -->
<!-- # V <- left_join(V,Full_OR_tab, by= join_by(variable==variable)) -->
<!-- #  -->
<!-- #  -->
<!-- # # For classification, ROC curve analysis is conducted on each predictor. For two class problems, a series of cutoffs is applied to the predictor data to predict the class. The sensitivity and specificity are computed for each cutoff and the ROC curve is computed. The trapezoidal rule is used to compute the area under the ROC curve. This area is used as the measure of variable importance -->
<!-- #  -->
<!-- # L <- ggplot2::ggplot(V, aes(x=reorder(variable,wt_scaled), y=wt_scaled)) + -->
<!-- # geom_point( color="blue", size=4, alpha=0.6)+ -->
<!-- # geom_segment( aes(x=variable, xend=variable, y=0, yend=wt_scaled),  -->
<!-- # color='skyblue') + -->
<!-- # xlab('Variable')+ -->
<!-- # ylab('Overall Importance (%) explained')+ -->
<!-- # theme_classic() + -->
<!-- # coord_flip()  -->
<!-- #  -->
<!-- # Wald_plot  <- wt_df |> -->
<!-- #       ggplot() + -->
<!-- #         geom_text(aes(x = 0, y = reorder(Variables,Raw.percent), label = Wald), hjust = 0) + -->
<!-- #         theme_void()  -->
<!-- #         # coord_cartesian(ylim = c(1,length(FP_dep$Variable))) -->
<!-- #        -->
<!-- # library(patchwork) -->
<!-- # layout <- c( -->
<!-- #   patchwork::area(t = 0, l = 0, b = 30, r = 21), -->
<!-- #   patchwork::area(t = 0, l = 16, b = 30, r = 30) -->
<!-- # ) -->
<!-- #  -->
<!-- # L + Wald_plot + plot_layout(design = layout) -->
<!-- ``` -->

<!-- ### relative weight analysis -->
<!-- ```{r} -->
<!-- install.packages('devtools') -->
<!-- devtools::install_github("martinctc/rwa") -->
<!-- #https://langtest.jp/shiny/rwa/ -->
<!-- library(rwa) -->

<!-- RWA <- mydata_B3 %>% -->
<!--   rwa(outcome = "Ex_rec", -->
<!--       predictors =  -->
<!--         c("Age", 'College',"White_Race", "Income_60k_plus", "Combat_Veteran",  -->
<!--       "TOTAL_TRAUMAS", "Obesity", "Athsma", "Chron_pain", "Diabetes", "Hrt_atk",  -->
<!--       "Hrt_dis", -->
<!--       "High_chol", "High_bld_press", "Osteoporosis", "Stroke", "AUD_Current",  -->
<!--       "DUD_Current", "MDD_Current", "PTSD_Current","GAD_Current"), -->
<!--       applysigns = TRUE, -->
<!--       plot = TRUE) -->

<!-- rwa::plot_rwa(RWA$result) -->
<!-- RWA$result -->


<!-- # RWA_plot <-  -->
<!--   ggplot2::ggplot(RWA$result, aes(x=reorder(Variables,Rescaled.RelWeight), y=Rescaled.RelWeight)) + -->
<!-- geom_point( color="blue", size=4, alpha=0.6)+ -->
<!-- geom_segment( aes(x=Variables, xend=Variables, y=0, yend=Rescaled.RelWeight),  -->
<!-- color='skyblue') + -->
<!-- xlab('Variable')+ -->
<!-- ylab('Overall Importance (%) explained')+ -->
<!-- theme_classic() + -->
<!-- coord_flip()  -->
<!-- ``` -->

<!-- RElative importance analysis -->
<!-- ```{r} -->
<!-- # library(relaimpo) -->
<!-- #  -->
<!-- #  -->
<!-- #   -->
<!-- # fit1 <- glm(MET_min~ -->
<!-- #              #Covariates -->
<!-- #              Age + College + White_Race  + -->
<!-- #              Income_60k_plus + Combat_Veteran +  -->
<!-- #              TOTAL_TRAUMAS + BMI +  -->
<!-- #              #Physical Health Conditions -->
<!-- #              Athsma + Chron_pain + Diabetes+ Hrt_atk + -->
<!-- #              Hrt_dis + High_chol + High_bld_press + Osteoporosis + Stroke + -->
<!-- #              #Mental Health conditions -->
<!-- #              AUD_Current + DUD_Current + MDD_Current + PTSD_Current + GAD_Current, -->
<!-- #              # Data -->
<!-- #              data =thesis_NHRVS, -->
<!-- #              # Specify weights -->
<!-- #              weights = weight) -->
<!-- #  -->
<!-- # relimp <- calc.relimp(fit1, type = "lmg", importance = TRUE) -->
<!-- # calc.relimp -->
<!-- # ?calc.relimp() -->
<!-- #  -->
<!-- # # View the structure of the relimp object -->
<!-- # str(relimp) -->
<!-- #   -->
<!-- # # Plot the relative importance of predictors -->
<!-- # plot(relimp) -->
<!-- #  -->
<!-- # #order of which variables are important -->
<!-- #  -->
<!-- #  -->
<!-- # impo_values<- unlist(relimp@lmg) -->
<!-- # attri <- attributes(impo_values) -->
<!-- # impo_order<- unlist(relimp@lmg.rank) -->
<!-- #  -->
<!-- # impo_df <- data.frame( -->
<!-- #   cbind( -->
<!-- #     vars = attri$names, -->
<!-- #     round(impo_values*100,2), -->
<!-- #     impo_order -->
<!-- #   ) -->
<!-- # ) -->
<!-- # colnames(impo_df) <- c("vars","R2","Order") -->
<!-- #  -->
<!-- # impo_df$R2 <- as.numeric(impo_df$R2) -->
<!-- # impo_df$Order <- as.numeric(impo_df$Order) -->
<!-- #  -->
<!-- # # ####### Bootstraped relimp -->
<!-- # #  -->
<!-- # # boot_rel <- boot.relimp(fit, type = "lmg",  -->
<!-- # #                         nboot = 10) -->
<!-- # #   -->
<!-- # # boot_eval <- booteval.relimp(boot_rel) -->
<!-- # # plot(boot_eval) -->
<!-- # #  -->
<!-- # #  -->
<!-- # #  -->
<!-- #  -->
<!-- # ggplot2::ggplot(impo_df, aes(x=reorder(vars,-Order),y=R2), -->
<!-- #                 ) + -->
<!-- #   geom_hline(yintercept = 1,linetype="dashed",alpha = .25) + -->
<!-- #   geom_hline(yintercept = .5,linetype="dashed",alpha = .25) + -->
<!-- #   geom_bar(stat = "identity", color = "Black") + -->
<!-- #   ggtitle("% Varaince (i.e., R^2) explaiend by predictors of Physical Activity") + -->
<!-- #   theme_classic() + -->
<!-- #   xlab('Variable')+ -->
<!-- #   ylab('% of Response Variance')+ -->
<!-- #   ylim(0,1.5)+ -->
<!-- #   geom_text(aes(label = R2), vjust =.5, hjust = -.5, color = "black")+ -->
<!-- #   coord_flip()  -->
<!-- #                -->
<!-- # ggplot2::ggplot(V, aes(x=reorder(rownames(V),Overall), y=Overall)) + -->
<!-- # geom_point( color="blue", size=4, alpha=0.6)+ -->
<!-- # geom_segment( aes(x=rownames(V), xend=rownames(V), y=0, yend=Overall),  -->
<!-- # color='skyblue') + -->
<!-- # xlab('Variable')+ -->
<!-- # ylab('Overall Importance')+ -->
<!-- # theme_light() + -->
<!-- # coord_flip()  -->
<!-- ``` -->

<!-- ```{r} -->
<!-- install.packages("bruceR") -->
<!-- library(bruceR) -->

<!-- mod_NHRVS <- thesis_NHRVS |> -->
<!--   mutate( -->
<!--     GAD_Current = recode(GAD_Current, -->
<!--       "0" = "1", -->
<!--       "1" = "2" -->
<!--     ), -->
<!--     Diabetes = recode(Diabetes, -->
<!--       "0" = "1", -->
<!--       "1" = "2" -->
<!--     ) -->
<!--   ) -->

<!-- str(mod_NHRVS$Diabetes) -->

<!-- thesis_NHRVS$High_bld_press -->

<!-- attri$names -->

<!-- ###MCS -->
<!-- #insignificant moderation -->
<!-- PROCESS(thesis_NHRVS, -->
<!--   x="High_bld_press", y="Ex_rec", mods = "MCS", covs = c("Age", "College", "White_Race", -->
<!--   "Income_60k_plus", "Combat_Veteran", "TOTAL_TRAUMAS", "BMI")  -->
<!-- ) -->

<!-- #nonsignficiant -->
<!-- PROCESS(thesis_NHRVS, -->
<!--   x="Diabetes", y="Ex_rec", mods = "MCS", covs = c("Age", "College", "White_Race", -->
<!--   "Income_60k_plus", "Combat_Veteran", "TOTAL_TRAUMAS", "BMI")  -->
<!-- ) -->

<!-- #Significant -->
<!-- PROCESS(thesis_NHRVS, -->
<!--   x="High_chol", y="Ex_rec", mods = "MCS", covs = c("Age", "College", "White_Race", -->
<!--   "Income_60k_plus", "Combat_Veteran", "TOTAL_TRAUMAS", "BMI")  -->
<!-- ) -->

<!-- #Significant -->
<!-- PROCESS(thesis_NHRVS, -->
<!--   x="GAD_Current", y="Ex_rec", mods = "PCS", covs = c("Age", "College", "White_Race", -->
<!--   "Income_60k_plus", "Combat_Veteran", "TOTAL_TRAUMAS", "BMI")  -->
<!-- ) -->

<!-- #nonsignficiant -->
<!-- PROCESS(thesis_NHRVS, -->
<!--   x="Diabetes", y="Ex_rec", mods = "MCS", covs = c("Age", "College", "White_Race", -->
<!--   "Income_60k_plus", "Combat_Veteran", "TOTAL_TRAUMAS", "BMI")   -->
<!-- ) -->
<!-- ``` -->

<!-- ## Interactions of health conditions on physical activity recomendations -->
<!-- ```{r} -->
<!-- # library(bruceR) -->
<!-- # # assign a vector of covariates to be used in analysis -->
<!-- # covs = c("Age", "College", "White_Race", -->
<!-- #   "Income_60k_plus", "Combat_Veteran", "TOTAL_TRAUMAS", "BMI") -->
<!-- #  -->
<!-- # ##### Diabetes -->
<!-- # PROCESS(thesis_NHRVS, # Data -->
<!-- #   x="Diabetes",  # Health conditoin -->
<!-- #   mods = "GAD_Current",  # Moderator -->
<!-- #   y="Ex_rec", # outcome variable -->
<!-- #   covs = covs) # covariates -->
<!-- #  -->
<!-- # PROCESS(thesis_NHRVS, -->
<!-- #   x="Diabetes", mods = "MDD_Current", -->
<!-- #   y="Ex_rec", -->
<!-- #   covs = covs) -->
<!-- #  -->
<!-- # PROCESS(thesis_NHRVS, -->
<!-- #   x="Diabetes", mods = "DUD_Current", -->
<!-- #   y="Ex_rec", -->
<!-- #   covs = covs) -->
<!-- #  -->
<!-- # #### Asthma -->
<!-- # PROCESS(thesis_NHRVS, -->
<!-- #   x="Athsma", mods = "Total_HC", -->
<!-- #   y="Ex_rec", -->
<!-- #   covs = covs) -->
<!-- #  -->
<!-- # ### Osteoporosis -->
<!-- #  -->
<!-- # PROCESS(thesis_NHRVS, -->
<!-- #   x="Osteoporosis", mods = "Total_HC", -->
<!-- #   y="Ex_rec", -->
<!-- #   covs = covs) -->
<!-- #  -->
<!-- # ### HRT Attack -->
<!-- #  -->
<!-- # PROCESS(thesis_NHRVS, -->
<!-- #   x="Hrt_atk", mods = "Total_HC", -->
<!-- #   y="Ex_rec", -->
<!-- #   covs = covs) -->
<!-- #  -->
<!-- # ### High cholesterol -->
<!-- #  -->
<!-- # PROCESS(thesis_NHRVS, -->
<!-- #   x="High_chol", mods = "Total_HC", -->
<!-- #   y="Ex_rec", -->
<!-- #   covs = covs) -->
<!-- #  -->
<!-- # PROCESS(thesis_NHRVS, -->
<!-- #   x="GAD_Current" , # Health condition -->
<!-- #   mods = "Total_HC", # moderator -->
<!-- #   y="Ex_rec", # outcome variable -->
<!-- #   covs = covs) -->
<!-- #  -->
<!-- # PROCESS(thesis_NHRVS, -->
<!-- #   x="MDD_Current", mods = "Total_HC", -->
<!-- #   y="Ex_rec", -->
<!-- #   covs = covs) -->
<!-- #  -->
<!-- # PROCESS(thesis_NHRVS, -->
<!-- #   x="Stroke", mods = "Total_HC", -->
<!-- #   y="Ex_rec", -->
<!-- #   covs = covs) -->
<!-- ``` -->

<!-- https://www.appsilon.com/post/r-logistic-regression -->
<!-- ROC. vs AUC -->
<!-- ```{r} -->
<!-- library('pROC') -->
<!-- Reg_df <- thesis_NHRVS |> -->
<!--   dplyr::select( -->
<!--     Ex_rec, -->
<!--              #Covariates -->
<!--              Age , College , White_Race  , -->
<!--              Income_60k_plus , Combat_Veteran ,  -->
<!--              TOTAL_TRAUMAS , BMI , -->
<!--              #Physical Health Conditions -->
<!--              Athsma , Chron_pain , Diabetes, Hrt_atk ,  -->
<!--              Hrt_dis , High_chol , High_bld_press , Osteoporosis , Stroke , -->
<!--              #Mental Health conditions -->
<!--              AUD_Current , DUD_Current , MDD_Current , PTSD_Current , GAD_Current, -->
<!--              # Data -->
<!--              weight) -->
<!-- Reg_df <-na.omit(Reg_df) -->

<!-- fit1<-glm(Ex_rec~ -->
<!--              #Covariates -->
<!--              Age + College + White_Race  + -->
<!--              Income_60k_plus + Combat_Veteran +  -->
<!--              TOTAL_TRAUMAS + BMI + -->
<!--              #Physical Health Conditions -->
<!--              Athsma + Chron_pain + Diabetes+ Hrt_atk +  -->
<!--              Hrt_dis + High_chol + High_bld_press + Osteoporosis + Stroke + -->
<!--              #Mental Health conditions -->
<!--              AUD_Current + DUD_Current + MDD_Current + PTSD_Current + GAD_Current, -->
<!--              # Data -->
<!--              data =Reg_df, -->
<!--              # Specify type of regression -->
<!--              family="binomial",weights = weight) -->


<!-- # just number of conditions -->
<!-- probabilities <-  predict(fit1, NewData=Reg_df ,type = "response") -->
<!-- predicted.classes <- ifelse(probabilities > 0.5, 1,0) -->

<!-- #confusion matrix -->
<!-- # table(HC_df$Ex_rec, predicted.classes) -->
<!-- #roc -->
<!-- roc1 <- roc(response = Reg_df$Ex_rec, -->
<!--                predictor = probabilities) -->

<!-- ggroc(roc1, legacy.axes = TRUE) + -->
<!--   labs(x = 'False-positive rate', y = 'True-positive rate', -->
<!--        title = 'ROC curve\nEx_rec ~ # Health Conditions + Covariates') + -->
<!--   annotate('text', x = .5, y = .5, label = paste0('AUC: ', round(auc(roc1), digits = 2))) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- #just number of conditions -->

<!-- HC_df <- thesis_NHRVS |> -->
<!--   dplyr::select( -->
<!--     #outcome -->
<!--     Ex_rec, -->
<!--     #covaraiates -->
<!--     Age,College,White_Race,Income_60k_plus,Combat_Veteran,TOTAL_TRAUMAS,BMI,   -->
<!--     #HC -->
<!--     Total_HC, -->
<!--     #weights -->
<!--     weight -->
<!--   )  -->

<!-- HC_df <- na.omit(HC_df) -->
<!-- library(caret) -->


<!-- fit2 <- glm(Ex_rec~ -->
<!--              #Covariates -->
<!--              Age + College + White_Race  + -->
<!--              Income_60k_plus + Combat_Veteran +  -->
<!--              TOTAL_TRAUMAS + BMI +  -->
<!--              #number of health conditions -->
<!--              Total_HC, -->
<!--              # Data -->
<!--              data =HC_df, -->
<!--              # Specify weights -->
<!--              family = "binomial", weights = weight) -->


<!-- #install.packages("pROC") -->
<!-- library(pROC) -->


<!-- # just number of conditions -->
<!-- probabilities <-  predict(fit2, NewData=HC_df ,type = "response") -->
<!-- predicted.classes <- ifelse(probabilities > 0.5, 1,0) -->

<!-- #confusion matrix -->
<!-- table(HC_df$Ex_rec, predicted.classes) -->
<!-- #roc -->
<!-- roc2 <- roc(response = HC_df$Ex_rec, -->
<!--                predictor = probabilities) -->

<!-- ggroc(roc2, legacy.axes = TRUE, col = "red") + -->
<!--   labs(x = 'False-positive rate', y = 'True-positive rate', -->
<!--        title = 'ROC curve\nEx_rec ~ # Health Conditions + Covariates') + -->
<!--   annotate('text', x = .5, y = .5, label = paste0('AUC: ', round(auc(roc2), digits = 2))) -->


<!-- both_df <- thesis_NHRVS |> -->
<!--   dplyr::select( -->
<!--     Ex_rec, -->
<!--              #Covariates -->
<!--              Age , College , White_Race  , -->
<!--              Income_60k_plus , Combat_Veteran ,  -->
<!--              TOTAL_TRAUMAS , BMI , -->
<!--              #Physical Health Conditions -->
<!--              Athsma , Chron_pain , Diabetes, Hrt_atk ,  -->
<!--              Hrt_dis , High_chol , High_bld_press , Osteoporosis , Stroke , -->
<!--              #Mental Health conditions -->
<!--              AUD_Current , DUD_Current , MDD_Current , PTSD_Current , GAD_Current, -->
<!--              Total_HC, -->
<!--              # Data -->
<!--              weight) -->
<!-- both_df <-na.omit(both_df) -->

<!-- fit3<-glm(Ex_rec~ -->
<!--              #Covariates -->
<!--              Age + College + White_Race  + -->
<!--              Income_60k_plus + Combat_Veteran +  -->
<!--              TOTAL_TRAUMAS + BMI + -->
<!--              #Physical Health Conditions -->
<!--              Athsma + Chron_pain + Diabetes+ Hrt_atk +  -->
<!--              Hrt_dis + High_chol + High_bld_press + Osteoporosis + Stroke + -->
<!--              #Mental Health conditions -->
<!--              AUD_Current + DUD_Current + MDD_Current + PTSD_Current + GAD_Current + -->
<!--              Total_HC, -->
<!--              # Data -->
<!--              data =both_df, -->
<!--              # Specify type of regression -->
<!--              family="binomial",weights = weight) -->


<!-- # just number of conditions -->
<!-- probabilities3 <-  predict(fit3, NewData=Both_df ,type = "response") -->
<!-- predicted.classes3 <- ifelse(probabilities3 > 0.5, 1,0) -->

<!-- #confusion matrix -->
<!-- table(HC_df$Ex_rec, predicted.classes3) -->
<!-- #roc -->
<!-- roc3 <- roc(response = both_df$Ex_rec, -->
<!--                predictor = probabilities3) -->

<!-- ggroc(roc3, legacy.axes = TRUE) + -->
<!--   labs(x = 'False-positive rate', y = 'True-positive rate', -->
<!--        title = 'ROC curve\nEx_rec ~ # Health Conditions + Conditions +  Covariates') + -->
<!--   annotate('text', x = .5, y = .5, label = paste0('AUC: ', round(auc(roc3), digits = 2))) -->
<!-- ``` -->

<!-- predictive probabilities  -->
<!-- ```{r} -->

<!-- HC_df <- thesis_NHRVS |> -->
<!--   dplyr::select( -->
<!--     #outcome -->
<!--     Ex_rec, -->
<!--     #covaraiates -->
<!--     Age,College,White_Race,Income_60k_plus,Combat_Veteran,TOTAL_TRAUMAS,BMI,   -->
<!--     #HC -->
<!--     Total_HC, -->
<!--     #weights -->
<!--     weight) -->
<!--   # ) |> -->
<!--   # mutate( -->
<!--   #   Ex_rec = as.factor(ifelse(Ex_rec == "Insufficient", 0,1)) -->
<!--   # ) -->
<!-- HC_df <- na.omit(HC_df) -->
<!-- library(caret) -->

<!-- fit2 <- glm(relevel(Ex_rec,ref = "Sufficient")~ -->
<!--              #Covariates -->
<!--              Age + College + White_Race  + -->
<!--              Income_60k_plus + Combat_Veteran +  -->
<!--              TOTAL_TRAUMAS + BMI +  -->
<!--              #number of health conditions -->
<!--              Total_HC, -->
<!--              # Data -->
<!--              data =HC_df, -->
<!--              # Specify weights -->
<!--              family = "binomial") #weights = weight) -->

<!-- OR <- round(exp(cbind(coef(fit2), confint(fit2))),2) -->

<!-- OR_fig <-paste0(OR[8,1], " [",OR[8,2], ",",OR[8,2], "]") -->

<!-- HC_df2$prob <- predict(fit2, NewData=HC_df ,type = "response") -->
<!-- HC_df2<- cbind(HC_df, predict(fit2, newdata = HC_df, type = "response", -->
<!--     se = TRUE)) -->

<!-- HC_df2 <- HC_df2 |> -->
<!--   mutate( -->
<!--     LL = fit - (1.96 * (se.fit), -->
<!--     UL = fit + (1.96 * se.fit) -->
<!--   ) -->

<!-- # just number of conditions -->
<!-- ggplot(HC_df2, aes(x = Total_HC, y = fit)) +  -->
<!--   #geom_ribbon(aes(ymin = LL, -->
<!--     # ymax = UL), alpha = 0.2) +  -->
<!--   geom_smooth(size = 1) + -->
<!--   labs(x = '# of co-occuring health conditions', y = 'Predictive probability for insuficient activity', -->
<!--        title = 'Predictive Probabilities\nExercise guidelines ~ # Health Conditions +  Covariates') + -->
<!--   #annotate('text', x = 10, y = .6, label = paste0('OR: ', OR_fig)) + -->
<!--   theme_classic() -->




<!-- ``` -->



<!-- ```{r} -->
<!-- # Read in simulated data -->
<!-- sim_dat <- read.csv('http://static.lib.virginia.edu/statlab/materials/data/roc_sim_dat.csv', header = T) -->

<!-- # See a few rows -->
<!-- sim_dat[c(1, 25, 75, 100), ] -->

<!-- sim_dat -->

<!-- # Use pROC calculate TPR/FPR across a range of classification thresholds -->
<!-- sim_roc <- roc(response = sim_dat$actual_outcome, -->
<!--                predictor = sim_dat$predicted_prob_of_Yes, -->
<!--                levels = c('No', 'Yes')) -->
<!-- # response: vector of actual outcomes -->
<!-- # predictor: vector of probabilities, one for each observation -->
<!-- # levels: response values to be taken as "No"/0/"Failure"/etc. and "Yes"/1/"Success"/etc., respectively -->

<!-- # Plot ROC curve -->
<!-- # - pROC::ggroc() prints the ROC curve using ggplot2; you can print the curve using base R graphics with pROC::plot.roc() -->
<!-- # - legacy.axes = TRUE ensures that the x-axis is displayed as FPR from 0 to 1 as opposed to -->
<!-- #     specificity (1-FPR) from 1 to 0 -->
<!-- ggroc(sim_roc, legacy.axes = TRUE) + -->
<!--   labs(x = 'False-positive rate', y = 'True-positive rate', title = 'Simulated ROC curve') -->








<!-- roc(train.data$Ex_rec, -->
<!--              predicted.classes) -->

<!-- \ -->




<!-- summary(test.data$Ex_rec) -->
<!-- ``` -->



<!-- ### Export Tables to CSV -->
<!-- ```{r} -->
<!-- write_csv(Ins_Mod, "~/Desktop/Coding/data/Ins_Mod.csv") -->
<!-- write_csv(Ins_Act, "~/Desktop/Coding/data/Ins_Act.csv") -->
<!-- write_csv(Act_Mod, "~/Desktop/Coding/data/Act_Mod.csv") -->
<!-- ``` -->


<!-- # Create Tables for Multinomial Logistic Regression Output  -->

<!-- We have everything we need for our final table output! -->
<!-- ```{r,message=FALSE} -->
<!-- #1. Import tables -->
<!--    r2_change <- read_csv("~/Desktop/Coding/data/R2change.csv") -->
<!--    cov.SF8_OR_tab <- read.csv("~/Desktop/Coding/data/SF8.cov_OR_tab.csv") -->
<!--    Ins_Mod <- read_csv("~/Desktop/Coding/data/Ins_Mod.csv") -->
<!--    Ins_Act <- read_csv("~/Desktop/Coding/data/Ins_Act.csv") -->
<!--    Act_Mod <- read_csv( "~/Desktop/Coding/data/Act_Mod.csv") -->
<!-- ``` -->


<!-- ```{r} -->
<!-- #2. Create dataframes to be merged. -->
<!--     OR_Table = data.frame( -->
<!--       Ins_Act$variable, Ins_Act$ci, Ins_Mod$ci, Act_Mod$ci,Act_Mod$r2_change -->
<!--       ) -->
<!--     colnames(OR_Table) <- c("Variable","IvA_ODDS", -->
<!--                           "IvM_ODDS", "AvM_ODDS", -->
<!--                           "R2_Change") -->

<!-- #3. Create a block 3 row -->
<!--   Block_3 = cbind( -->
<!--     Variable = "Block 3: Health Conditions R^2 range = 0.032 - 0.052", -->
<!--     IvA_ODDS = NA, -->
<!--     IvM_ODDS = NA, -->
<!--     AvM_ODDS = NA, -->
<!--     R2_Change = NA -->
<!--   ) -->

<!-- #4. pull out values from covariates table -->
<!--   Cov_table = data.frame( -->
<!--     Full_OR_tab$variable, -->
<!--     Full_OR_tab$IvA_ODDS,  -->
<!--     Full_OR_tab$IvM_ODDS, -->
<!--     Full_OR_tab$AvM_ODDS -->
<!--   ) -->
<!--   Cov_table$R2_Change = NA -->
<!--   colnames(Cov_table) <- c("Variable","IvA_ODDS", -->
<!--                           "IvM_ODDS", "AvM_ODDS", -->
<!--                           "R2_Change") -->

<!-- #5. Merge all the data frames -->
<!--   OR_Table <- rbind(Cov_table,Block_3,OR_Table) -->

<!-- #6. update R2 change df and add it to OR tab -->
<!--   r2_change = rbind(r2_change[1:6,],NA,r2_change[7:33,]) -->
<!--   OR_Table <- cbind(OR_Table[,1:4],r2_change) -->

<!-- #6. Rename columns for table  -->
<!--   colnames(OR_Table) <- c("Variable","Insufficient vs Sufficient ORs", -->
<!--                           "Insufficient vs Moderate ORs", "Active vs Moderate ORs", "R^2 Change") -->


<!-- #7. View Table -->
<!--     knitr::kable(OR_Table) %>% -->
<!--           kable_styling(bootstrap_options = c("striped", "hover", "condensed")) -->

<!-- #8 Export Table -->
<!--     write_csv(OR_Table,"~/Desktop/Coding/data/Thesis_OR_Table.csv") -->

<!-- ``` -->

<!-- ```{r} -->

<!-- ``` -->


<!-- Multicolinearity Analysis -->
<!-- ```{r} -->
<!-- library(tidyverse) -->
<!-- library(dplyr) -->
<!-- library(ggplot) -->
<!-- library(ggcorrplot) -->

<!-- thesis_NHRVS$Hrt_dis -->
<!-- ``` -->


<!-- ```{r} -->
<!-- #physical health conditions -->
<!-- corr1 <- thesis_NHRVS |> -->
<!--   dplyr::select(Ex_3cat,Any_Disability, Age, College , Income_60k_plus, YN_work , BMI , MCS -->
<!--     ) -->

<!-- model.matrix(~0+., data=corr1) %>%  -->
<!--   cor(use="pairwise.complete.obs") %>%  -->
<!--   ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2) -->

<!-- # mental health conditions -->
<!-- corr2 <- thesis_NHRVS |> -->
<!--   dplyr::select(Ex_3cat,LT_MDD, Age, College , Income_60k_plus, YN_work , BMI , PCS -->
<!--     ) -->

<!-- model.matrix(~0+., data=corr2) %>%  -->
<!--   cor(use="pairwise.complete.obs") %>%  -->
<!--   ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2) -->

<!-- ``` -->

